---
title: "TumorMeta_Sun_2023_OtherMethods"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

Benchmarking analyses against widely used CCC methods, including CellChat, ICELLNET, and exFINDER.

For each cluster identified by Seurat162, the top 10 marker genes were used as input target genes for OrganChat and exFINDER. Then the LS-T SigNet between clusters was inferred by OrganChat, and the ligand-target regulatory network was provided by exFINDER and its own database. The CellChat analysis was done based on its standard workflow, while the p-value threshold (thresh.p) in the identifyOverExpressedGenes function was set to 1 to include all inferred ligand-receptor pairs. For ICELLNET, the receiver cells were set to be all measured cells to infer all possible communications between clusters, then the analysis was performed following its standard workflow.

# Preparation

```{r}
library(OrganChat)

library(RColorBrewer)
library(survival)
library(pheatmap)
```


```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"    # your path to the ouput folder
```


Load data sets and marker gene list
```{r, include=FALSE}
seurat_MSI <- readRDS(paste0(data.path, "seurat_MSI.rds"))
seurat_RNA <- readRDS(paste0(data.path, "seurat_RNA.rds"))

seurat_RNA_markers <- read_csv(paste0(data.path, "seurat_RNA_markers.csv"))

Idents(seurat_MSI) = seurat_MSI@meta.data$cell_type
Idents(seurat_RNA) = seurat_RNA@meta.data$cell_type
```


# OC analysis

Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_human.rda"))
load(paste0(DB.path, "RSE_layer2_human.rda"))
load(paste0(DB.path, "SET_layer3_human.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_human
OrganChatDB[[2]] <- RSE_layer2_human
OrganChatDB[[3]] <- SET_layer3_human
```

# OrganChat analysis between two assigned organs

Prepare input data sets
```{r}
Data_organ1 <- subset(seurat_RNA, subset = organ == "organ1")
Data_organ2 <- subset(seurat_RNA, subset = organ == "organ2")

Data_organ1@meta.data$cell_type <- fct_drop(Data_organ1@meta.data$cell_type)
Data_organ2@meta.data$cell_type <- fct_drop(Data_organ2@meta.data$cell_type)

Idents(Data_organ1) = Data_organ1@meta.data$cell_type
Idents(Data_organ2) = Data_organ2@meta.data$cell_type

data.list = list(data1 = Data_organ1@assays$RNA@data, data2 = Data_organ2@assays$RNA@data)
idents.list = list(idents1 = Data_organ1@active.ident, idents2 = Data_organ2@active.ident)
```

Create OrganChat object
```{r}
OC.test = create_OrganChat(object = data.list, 
                          organs = c("organ1", "organ2"), 
                          idents.list = idents.list,
                          ComparisonAnalysis = FALSE,
                          assay = NULL, 
                          do.sparse = T)
```

Prepare the input scMETA data
```{r}
scMETA_organ1 <- subset(seurat_MSI, subset = organ == "organ1")
scMETA_organ2 <- subset(seurat_MSI, subset = organ == "organ2")

scMETA_organ1@meta.data$cell_type <- fct_drop(scMETA_organ1@meta.data$cell_type)
scMETA_organ2@meta.data$cell_type <- fct_drop(scMETA_organ2@meta.data$cell_type)

Idents(scMETA_organ1) = scMETA_organ1@meta.data$cell_type
Idents(scMETA_organ2) = scMETA_organ2@meta.data$cell_type
```


Integrate scMeta data
```{r}
OC.test = cal_scMeta.bygroup(object = OC.test,
                        scMeta.data = scMETA_organ1@assays$RNA@data,
                        organ.name = "organ1",
                        idents = scMETA_organ1@active.ident,
                        mean_method = NULL)

OC.test = cal_scMeta.bygroup(object = OC.test,
                        scMeta.data = scMETA_organ2@assays$RNA@data,
                        organ.name = "organ2",
                        idents = scMETA_organ2@active.ident,
                        mean_method = NULL)
```

Use the RNA data to calculate the mean expression of the DG(downstream gene) and LS(long-range signal)
```{r}
OC.test = cal_scRNA.bygroup(object = OC.test,
                       DB = OrganChatDB,
                       mean_method = NULL,
                       scale.max = 10)
```

Select the top 10 markers of every cluster
```{r}
seurat_RNA_markers %>%
  group_by(cluster) %>%
  slice_head(n = 10) %>%
  ungroup() -> top10

target.test =  unique(top10$gene)

OC.test = OCnet0_infer(object = OC.test, 
                  DB = OrganChatDB, 
                  LS = NULL, 
                  receptor = NULL, 
                  tf = NULL,
                  target = target.test,
                  single.condition = TRUE)
```


OC inferred signals & receptors
```{r}
OC.signal <- unique(OC.test@net0$LS)
OC.receptor <- unique(OC.test@net0$Receptor)
```



# CellChat analysis

```{r, include=FALSE}
library(CellChat)
library(patchwork)
options(stringsAsFactors = FALSE)
```


```{r, include=FALSE}
data.input <- seurat_RNA[["RNA"]]@data # normalized data matrix
# For Seurat version >= “5.0.0”, get the normalized data via `seurat_object[["RNA"]]$data`
labels <- Idents(seurat_RNA)
meta <- data.frame(labels = labels, row.names = names(labels)) # create a dataframe of the cell labels

# create CC object
cellchat <- createCellChat(object = seurat_RNA, group.by = "ident", assay = "RNA")

# assign CCDB
CellChatDB <- CellChatDB.human # use CellChatDB.mouse if running on mouse data
CellChatDB.use <- CellChatDB
cellchat@DB <- CellChatDB.use

cellchat <- subsetData(cellchat) # This step is necessary even if using the whole database
future::plan("multisession", workers = 4) # do parallel
cellchat <- identifyOverExpressedGenes(cellchat, thresh.p = 1)
cellchat <- identifyOverExpressedInteractions(cellchat)

# CC analysis
cellchat <- computeCommunProb(cellchat, type = "triMean")
cellchat <- filterCommunication(cellchat, min.cells = 10)
cellchat <- computeCommunProbPathway(cellchat)
cellchat <- aggregateNet(cellchat)
```

Export the inferred ligands and receptors
```{r}
x = cellchat@LR$LRsig$interaction_name
x.split <- str_split(x, fixed("_"))

CC.ligand = c()
CC.receptor = c()

for (i in 1:length(x.split)) {
  CC.ligand <- c(CC.ligand, x.split[[i]][1])
  
  for (j in 2:length(x.split[[i]]) ) {
    CC.receptor <- c(CC.receptor, x.split[[i]][j])
  }
}

CC.ligand <- unique(CC.ligand)
CC.receptor <- unique(CC.receptor)
```



# ICELLNET analysis

```{r, include=FALSE}
library(BiocGenerics)
library("org.Hs.eg.db")
library("hgu133plus2.db")
library(jetset)
library(icellnet)
library(gridExtra)

db=as.data.frame(read.csv(curl::curl(url="https://raw.githubusercontent.com/soumelis-lab/ICELLNET/master/data/ICELLNETdb.tsv"), sep="\t",header = T, check.names=FALSE, stringsAsFactors = FALSE, na.strings = ""))
               
db.name.couple=name.lr.couple(db, type="Family")
head(db.name.couple)
```


```{r}
data <- as.data.frame(GetAssayData(seurat_RNA, layer = "data")) #or other matrix for which features expression values # are scaled by the total expression in each cell

target <- seurat_RNA@meta.data
target$Type=seurat_RNA$cell_type
target$Class=seurat_RNA$cell_type
target$Cell=rownames(target)

average.manual=matrix(ncol=length(unique(target$Type)), nrow=length(rownames(data)))
colnames(average.manual)=unique(target$Type)
rownames(average.manual)=rownames(data)
dim(average.manual)
for (cell in unique(target$Type)){
  cells.clust=target$Cell[which(target$Type==cell)]
  average.manual[,cell]=apply(data[,which(colnames(data)%in%cells.clust)], 1, mean)
}

average.clean=average.manual
```

direction = "out"
```{r}
data.icell=as.data.frame(gene.scaling(as.data.frame(average.clean), n=1, db=db))

PC.data=as.data.frame(data.icell[, c(unique(seurat_RNA$cell_type), "Symbol")], row.names = rownames(data.icell))
my.selection = unique(seurat_RNA$cell_type)

score.computation.1= icellnet.score(direction="out", PC.data=PC.data, 
                                    CC.data= as.data.frame(data.icell[, unique(seurat_RNA$cell_type)], 
                                                           row.names = rownames(data.icell)),  
                                    PC=my.selection, CC.type = "RNAseq", 
                                    PC.type = "RNAseq",  db = db)
score1=as.data.frame(score.computation.1[[1]])
lr1=score.computation.1[[2]]
```


Export the inferred ligands and receptors
```{r}
lr_data <- data.frame(lr_name = rownames(lr1), value = lr1) 
    
text <- lr_data$lr_name
text <- gsub(" ", "", text, fixed=TRUE)
text <- str_split(text, fixed("/"))
n <- length(text)

text_ligands <- c()
text_receptors <- c()
    
for (k in 1:n) {
  text_ligands <- c(text_ligands, text[[k]][1])
  text_receptors <- c(text_receptors, text[[k]][2])
}
   
text_ligands = text_ligands[!duplicated(text_ligands)]
text_ligands <- str_split(text_ligands, fixed("+"))

text_receptors = text_receptors[!duplicated(text_receptors)]
text_receptors <- str_split(text_receptors, fixed("+"))
    
ICELLNET.ligand <- c()
ICELLNET.receptor <- c()

for (k in 1:length(text_ligands)) {
  if (length(text_ligands[[k]]) == 1){
    ICELLNET.ligand <- c(ICELLNET.ligand, text_ligands[[k]])
  }else{ ICELLNET.ligand <- c(ICELLNET.ligand, text_ligands[[k]][1:length(text_ligands[[k]])]) }
}


for (k in 1:length(text_receptors)) {
  if (length(text_receptors[[k]]) == 1){
    ICELLNET.receptor <- c(ICELLNET.receptor, text_receptors[[k]])
  }else{ ICELLNET.receptor <- c(ICELLNET.receptor, text_receptors[[k]][1:length(text_receptors[[k]])]) }
}

ICELLNET.ligand.in <- unique(ICELLNET.ligand)
ICELLNET.receptor.in <- unique(ICELLNET.receptor)
```


direction = "in"
```{r}
data.icell=as.data.frame(gene.scaling(as.data.frame(average.clean), n=1, db=db))

PC.data=as.data.frame(data.icell[, c(unique(seurat_RNA$cell_type), "Symbol")], row.names = rownames(data.icell))
my.selection = unique(seurat_RNA$cell_type)

score.computation.2= icellnet.score(direction="in", PC.data=PC.data, 
                                    CC.data= as.data.frame(data.icell[, unique(seurat_RNA$cell_type)], 
                                                           row.names = rownames(data.icell)),  
                                    PC=my.selection, CC.type = "RNAseq", 
                                    PC.type = "RNAseq",  db = db)
score2=as.data.frame(score.computation.2[[1]])
lr2=score.computation.2[[2]]
```


Export the inferred ligands and receptors
```{r}
lr_data <- data.frame(lr_name = rownames(lr2), value = lr2) 
    
text <- lr_data$lr_name
text <- gsub(" ", "", text, fixed=TRUE)
text <- str_split(text, fixed("/"))
n <- length(text)

text_ligands <- c()
text_receptors <- c()
    
for (k in 1:n) {
  text_ligands <- c(text_ligands, text[[k]][1])
  text_receptors <- c(text_receptors, text[[k]][2])
}
   
text_ligands = text_ligands[!duplicated(text_ligands)]
text_ligands <- str_split(text_ligands, fixed("+"))

text_receptors = text_receptors[!duplicated(text_receptors)]
text_receptors <- str_split(text_receptors, fixed("+"))
    
ICELLNET.ligand <- c()
ICELLNET.receptor <- c()

for (k in 1:length(text_ligands)) {
  if (length(text_ligands[[k]]) == 1){
    ICELLNET.ligand <- c(ICELLNET.ligand, text_ligands[[k]])
  }else{ ICELLNET.ligand <- c(ICELLNET.ligand, text_ligands[[k]][1:length(text_ligands[[k]])]) }
}


for (k in 1:length(text_receptors)) {
  if (length(text_receptors[[k]]) == 1){
    ICELLNET.receptor <- c(ICELLNET.receptor, text_receptors[[k]])
  }else{ ICELLNET.receptor <- c(ICELLNET.receptor, text_receptors[[k]][1:length(text_receptors[[k]])]) }
}

ICELLNET.ligand.out <- unique(ICELLNET.ligand)
ICELLNET.receptor.out <- unique(ICELLNET.receptor)
```


merge
```{r}
ICELLNET.ligand <- unique( c(ICELLNET.ligand.in, ICELLNET.ligand.out) )
ICELLNET.receptor <- unique( c(ICELLNET.receptor.in, ICELLNET.receptor.out) )
```


################################################################################

# exFINDER analysis

```{r, include=FALSE}
library(exFINDER)
```

~/Documents/OrganChat_v3/exFINDERmaster2
```{r}
# load exFINDER database
load("~/Documents/OrganChat_v3/exFINDERmaster2/data/LR_layer1_human.rda")
load("~/Documents/OrganChat_v3/exFINDERmaster2/data/RTF_layer2_human.rda")
load("~/Documents/OrganChat_v3/exFINDERmaster2/data/TFT_layer3_human.rda")

exFINDER.H <- list()
exFINDER.H[[1]] <- LR_layer1_human
exFINDER.H[[2]] <- RTF_layer2_human
exFINDER.H[[3]] <- TFT_layer3_human
```


```{r}
exp.data <- seurat_RNA@assays$RNA@data
meta.data <- seurat_RNA@meta.data
meta.data$Type <- meta.data$cell_type

ltGRN <- get_ltGRN(Target = target.test, DB = exFINDER.H)
```


```{r}
exFINDER.ligand = unique( ltGRN$Graph.Node$Gene[ltGRN$Graph.Node$Role == "Ligand"] )
exFINDER.receptor = unique( ltGRN$Graph.Node$Gene[ltGRN$Graph.Node$Role == "Receptor"] )
```


################################################################################

# Visualization

```{r}
Signal.list = list(OC = OC.signal, CC = CC.ligand, ICELLNET = ICELLNET.ligand, exFINDER = exFINDER.ligand)
Receptor.list = list(OC = OC.receptor, CC = CC.receptor, ICELLNET = ICELLNET.receptor, exFINDER = exFINDER.receptor)
```


```{r}
unique.pct = c()
for (i in 1:3) {
  pct = 1 - length(intersect(Signal.list[[1]], Signal.list[[i+1]]))/length(Signal.list[[1]])
  unique.pct = c(unique.pct, pct)
}

for (i in 1:3) {
  pct = 1 - length(intersect(Receptor.list[[1]], Receptor.list[[i+1]]))/length(Receptor.list[[1]])
  unique.pct = c(unique.pct, pct)
}

pct.df_1 = data.frame(value = unique.pct, 
                    name = c(rep(c("CellChat", "ICELLNET", "exFINDER"), 2)),
                    category = c(rep("Signal/Ligand", 3), rep("Receptor", 3)))
pct.df_1$result = "uncovered"

pct.df_2 = data.frame(value = 1- unique.pct, 
                    name = c(rep(c("CellChat", "ICELLNET", "exFINDER"), 2)),
                    category = c(rep("Signal/Ligand", 3), rep("Receptor", 3)))
pct.df_2$result = "covered"

pct.df <- rbind(pct.df_1, pct.df_2)
pct.df$ID <- paste0(pct.df$name, "_", pct.df$category)
pct.df$name <- factor(pct.df$name, levels = c("CellChat", "ICELLNET", "exFINDER"))
pct.df$ID <- factor(pct.df$ID, levels = c("CellChat_Signal/Ligand", "CellChat_Receptor", 
                                          "ICELLNET_Signal/Ligand", "ICELLNET_Receptor",
                                          "exFINDER_Signal/Ligand", "exFINDER_Receptor"))
```


```{r}
# Stacked + percent
p = ggplot(pct.df, aes(fill=result, y=value, x=ID)) + 
  geom_bar(width = 0.7, position=position_stack(), stat="identity") +
  scale_fill_manual(values = c("#B0E2FF", "#FF7F50")) + 
  theme_minimal() + 
  theme(plot.background = element_rect(fill = "white") ,
        panel.grid.minor = element_blank())

p
# ggsave(p, filename=paste0(output.dir, "MethodCompare_Barplot_1.pdf") )
```


```{r}
LS.pct = c()
for (i in 1:3) {
  pct = 1 - length(intersect(unique(OrganChatDB[[1]]$from), Signal.list[[i+1]]))/length(Signal.list[[i+1]])
  LS.pct = c(LS.pct, pct)
}

for (i in 1:3) {
  pct = 1 - length(intersect(unique(OrganChatDB[[1]]$to), Receptor.list[[i+1]]))/length(Receptor.list[[i+1]])
  LS.pct = c(LS.pct, pct)
}

LSpct.df_1 = data.frame(value = LS.pct, 
                    name = c(rep(c("CellChat", "ICELLNET", "exFINDER"), 2)),
                    category = c(rep("Signal/Ligand", 3), rep("Receptor", 3)))
LSpct.df_1$result = "non-LS"

LSpct.df_2 = data.frame(value = 1- LS.pct, 
                    name = c(rep(c("CellChat", "ICELLNET", "exFINDER"), 2)),
                    category = c(rep("Signal/Ligand", 3), rep("Receptor", 3)))
LSpct.df_2$result = "LS"

LSpct.df <- rbind(LSpct.df_1, LSpct.df_2)
LSpct.df$ID <- paste0(LSpct.df$name, "_", LSpct.df$category)
LSpct.df$name <- factor(LSpct.df$name, levels = c("CellChat", "ICELLNET", "exFINDER"))
LSpct.df$ID <- factor(LSpct.df$ID, levels = c("CellChat_Signal/Ligand", "CellChat_Receptor", 
                                          "ICELLNET_Signal/Ligand", "ICELLNET_Receptor",
                                          "exFINDER_Signal/Ligand", "exFINDER_Receptor"))
```


```{r}
# Stacked + percent
p = ggplot(LSpct.df, aes(fill=result, y=value, x=ID)) + 
  geom_bar(width = 0.7, position=position_stack(), stat="identity") + 
  scale_fill_manual(values = c("#90EE90", "#F4A460")) +
  theme_minimal() + 
  theme(plot.background = element_rect(fill = "white") ,
        panel.grid.minor = element_blank())

p
# ggsave(p, filename=paste0(output.dir, "MethodCompare_Barplot_2.pdf") )
```





