---
title: "TumorMeta_Sun_2023_OC"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

Visualize the data abd perform OrganChat analysis between two “pseudo-organs” grouped based on cluster identity and spatial context. Group A: muscularis mucosa, peritumoral muscularis, and tumor tissue cells, while Group B: blood-containing tissue, intestinal metaplasia, lamina propria, and normal epithelium cells.

The original data comes from the following paper: Sun, C., Wang, A., Zhou, Y. et al. Spatially resolved multi-omics highlights cell-specific metabolic remodeling and interactions in gastric cancer. Nat Commun 14, 2692 (2023). https://doi.org/10.1038/s41467-023-38360-5.


```{r}
library(OrganChat)
library(dittoSeq)
library(RColorBrewer)
```


# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"    # your path to the ouput folder
```


Load data sets and marker gene list
```{r, include=FALSE}
# The two objects below contains spacial info for visualization
seurat_MSI_DimPLot <- readRDS(paste0(data.path, "TumorMeta_Sun_2023_seurat_MSI_DimPLot.rds"))
seurat_RNA_DimPLot <- readRDS(paste0(data.path, "TumorMeta_Sun_2023_seurat_RNA_DimPLot.rds"))

# The two objects below are simplified by removing unnecessary assays for OrganChat analysis to improve computational effeciency
seurat_MSI <- readRDS(paste0(data.path, "seurat_MSI.rds"))
seurat_RNA <- readRDS(paste0(data.path, "seurat_RNA.rds"))

seurat_RNA_markers <- read_csv(paste0(data.path, "seurat_RNA_markers.csv"))
```

################################################################################

# DimPlot

```{r}
seurat_RNA_DimPLot@meta.data$cell_type = factor(seurat_RNA_DimPLot@meta.data$cell_type, 
                                                levels = c("Blood-containing tissue",
                                                           "Intestinal metaplasia",
                                                           "Lamina propria",
                                                           "Normal epithelium",
                                                           "Muscularis mucosa",
                                                           "Peritumoral muscularis",
                                                           "Tumor tissue"))

dittoDimPlot(seurat_RNA_DimPLot, 
             var = "cell_type", 
             reduction.use = "umap", 
             size = 2,
             do.label = F,
             show.axes.numbers = F,
             xlab = NULL,
             ylab = NULL,
             color.panel = brewer.pal(8, "Set1")[1:7])
```


```{r}
seurat_RNA_DimPLot@meta.data$LRC = factor(seurat_RNA@meta.data$LRC)

dittoDimPlot(seurat_RNA_DimPLot, 
             var = "LRC", 
             reduction.use = "umap", 
             size = 2,
             do.label = F,
             show.axes.numbers = F,
             xlab = NULL,
             ylab = NULL,
             color.panel = c("#C9C9C9", "#FF3030"))
```


# OrganChat analysis between two assigned groups


Load metabolite dictionary data
```{r, include=FALSE}
hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```

Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_human.rda"))
load(paste0(DB.path, "RSE_layer2_human.rda"))
load(paste0(DB.path, "SET_layer3_human.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_human
OrganChatDB[[2]] <- RSE_layer2_human
OrganChatDB[[3]] <- SET_layer3_human
```


Prepare input data sets
```{r}
Data_organ1 <- subset(seurat_RNA, subset = organ == "organ1")
Data_organ2 <- subset(seurat_RNA, subset = organ == "organ2")

Data_organ1@meta.data$cell_type <- fct_drop(Data_organ1@meta.data$cell_type)
Data_organ2@meta.data$cell_type <- fct_drop(Data_organ2@meta.data$cell_type)

Idents(Data_organ1) = Data_organ1@meta.data$cell_type
Idents(Data_organ2) = Data_organ2@meta.data$cell_type

data.list = list(data1 = Data_organ1@assays$RNA@data, data2 = Data_organ2@assays$RNA@data)
idents.list = list(idents1 = Data_organ1@active.ident, idents2 = Data_organ2@active.ident)
```


Create OrganChat object
```{r}
OC = create_OrganChat(object = data.list, 
                          organs = c("organ1", "organ2"), 
                          idents.list = idents.list,
                          ComparisonAnalysis = FALSE,
                          assay = NULL, 
                          do.sparse = T)
```

Prepare the input scMETA data
```{r}
scMETA_organ1 <- subset(seurat_MSI, subset = organ == "organ1")
scMETA_organ2 <- subset(seurat_MSI, subset = organ == "organ2")

scMETA_organ1@meta.data$cell_type <- fct_drop(scMETA_organ1@meta.data$cell_type)
scMETA_organ2@meta.data$cell_type <- fct_drop(scMETA_organ2@meta.data$cell_type)

Idents(scMETA_organ1) = scMETA_organ1@meta.data$cell_type
Idents(scMETA_organ2) = scMETA_organ2@meta.data$cell_type
```


Integrate scMeta data
```{r}
OC = cal_scMeta.bygroup(object = OC,
                        scMeta.data = scMETA_organ1@assays$RNA@data,
                        organ.name = "organ1",
                        idents = scMETA_organ1@active.ident,
                        mean_method = NULL)

OC = cal_scMeta.bygroup(object = OC,
                        scMeta.data = scMETA_organ2@assays$RNA@data,
                        organ.name = "organ2",
                        idents = scMETA_organ2@active.ident,
                        mean_method = NULL)
```

Use the RNA data to calculate the mean expression of the DG(downstream gene) and LS(long-range signal)
```{r}
OC = cal_scRNA.bygroup(object = OC,
                       DB = OrganChatDB,
                       mean_method = NULL,
                       scale.max = 10)
```

Select the top markers of the "Peritumoral muscularis" and "Muscularis mucosa"
```{r}
seurat_RNA_markers %>%
  group_by(cluster) %>%
  slice_head(n = 50) %>%
  ungroup() -> topmarkers

target =  unique( topmarkers$gene[ topmarkers$cluster %in% c("Peritumoral muscularis", "Muscularis mucosa", "Tumor tissue")] )
# target = unique(topmarkers$gene)

OC = OCnet0_infer(object = OC, 
                  DB = OrganChatDB, 
                  LS = NULL, 
                  receptor = NULL, 
                  tf = NULL,
                  target = target,
                  single.condition = TRUE)
```

Filter the network
```{r}
OC = filter_OCnet0(object = OC, cutoff_value = c(0, 0.2, 0.2, 0.2), single.condition = TRUE)
```

Calculate the chatP
```{r}
OC = cal_netchat_prob(object = OC, K = 0.1, N = 1, 
                      single.condition = TRUE)
```

Bootstrap test
```{r}
OC = cal_netchat_bootstrap(object = OC, R = 5, sd_cutoff = Inf, p_cutoff = NULL, 
                           single.condition = TRUE)
```


# Visualization

river plot: organ1 (Muscularis mucosa) -> organ1 (Tumor tissue), self communication
```{r}
df.plot = OC@net$Condition1$self_organ1$`organ1_Muscularis mucosa_to_Tumor tissue`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


river plot: organ2 (Intestinal metaplasia) -> organ1 (Tumor tissue)
```{r}
df.plot = OC@net$Condition1$backward$`Intestinal metaplasia_to_Tumor tissue`

OC_riverplot(df = df.plot,
             pref = "chatP",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


river plot: organ2 (Normal epithelium) -> organ1 (Tumor tissue)
```{r}
df.plot = OC@net$Condition1$backward$`Normal epithelium_to_Tumor tissue`

OC_riverplot(df = df.plot,
             pref = "chatP",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


river plot: organ1 (Peritumoral muscularis) -> organ1 (Tumor tissue), self communication
```{r}
df.plot = OC@net$Condition1$self_organ1$`organ1_Peritumoral muscularis_to_Tumor tissue`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


chord diagram: average weight (average communication probability) of LS-T pathways in organ2 -> organ1 communication on cluster level.
```{r}
OC_chorddiagram(object = OC,
                net = OC@net$Condition1$backward, # a list of sig network of one direction
                dir = "backward",
                category = "All",
                style = "ave.weight")
```


chord diagram: average weight (average communication probability) of LS-T pathways in organ1 -> organ1 communication on cluster level.
```{r}
OC_chorddiagram(object = OC,
                net = OC@net$Condition1$self_organ1, # a list of sig network of one direction
                dir = "self_organ1",
                category = "All",
                style = "ave.weight")
```



bubble heat map: organ2 -> organ1 communication
```{r}
OC_bubbleheatmap(object = OC,
                net = OC@net$Condition1$backward, # a list of sig network of one direction
                dir = "backward",
                category = "All",
                size = "total.counts",
                color = "total.chatP")
```


bubble heat map: organ1 -> organ1 communication
```{r}
OC_bubbleheatmap(object = OC,
                net = OC@net$Condition1$self_organ1, # a list of sig network of one direction
                dir = "self_organ1",
                category = "All",
                size = "total.counts",
                color = "total.chatP")
```


bubble heat map: organ2 -> organ2 communication
```{r}
OC_bubbleheatmap(object = OC,
                net = OC@net$Condition1$self_organ2, # a list of sig network of one direction
                dir = "self_organ2",
                category = "All",
                size = "total.counts",
                color = "total.chatP")
```


tree plot of the selected GRN in organ1 (Tumor tissue) -> organ1 (Tumor tissue) communication
```{r}
df.plot = OC@net$Condition1$self_organ1$`organ1_Tumor tissue_to_Tumor tissue`
x = construct_Network_df(df = df.plot,
                         category = "All",
                         restrict.by = "Both")
network_treeplot(x)
```


rose diagram: signaling inflow/outflow of organ2 (Normal epithelium) -> organ1 (Tumor tissue) communication
```{r}
components_rosediagram(df = OC@net$Condition1$backward$`Normal epithelium_to_Tumor tissue`, 
                       category = "All",
                       n = 5)
```








