---
title: "TumorMeta_Sun_2023_Perturbation_CAOC"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

Perturbation-based validation on two LS-receptor pairs by manually down-regulating LGALS1-LGALS3BP and up-regulating adenine-HNRNPA2B1, while retaining MIF-CD74 as the unperturbed control.

OrganChat analyses were conducted under both perturbed and control conditions, and the differential index (DI) of the pathways LGALS1-LGALS3BP-PCBP2-MALAT1, adenine-HNRNPA2B1-YBX1-FBL, and MIF-CD74-HNRNPK-NEAT1 was computed and averaged across clusters and conditions.

```{r}
library(OrganChat)

library(RColorBrewer)
library(survival)
library(pheatmap)
```

# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/TumorMeta_Sun_2023/"    # your path to the ouput folder
```

Load data sets and marker gene list
```{r, include=FALSE}
seurat_MSI <- readRDS(paste0(data.path, "seurat_MSI.rds"))
seurat_RNA <- readRDS(paste0(data.path, "seurat_RNA.rds"))

seurat_RNA_markers <- read_csv(paste0(data.path, "seurat_RNA_markers.csv"))
```

Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```

Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_human.rda"))
load(paste0(DB.path, "RSE_layer2_human.rda"))
load(paste0(DB.path, "SET_layer3_human.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_human
OrganChatDB[[2]] <- RSE_layer2_human
OrganChatDB[[3]] <- SET_layer3_human
```

# Perturbation

For OrganChat validation, two LS-receptor pairs (LGALS1-LGALS3BP and Adenine-HNRNPA2B1) were manually perturbed: 
(1) Half of the spots in the muscularis mucosa and tumor tissue were randomly selected for perturbation. 
(2) The expression levels of LGALS1 in muscularis mucosa and LGALS3BP in tumor tissue were downscaled to 0.1x of their original levels, whereas the abundance of Adenine in the muscularis mucosa and the expression of HNRNPA2B1 in tumor tissue were upscaled 10×.
(3) To evaluate robustness, we introduced multiplicative Gaussian noise to the original value A.

```{r, include=FALSE}
round = 20

target.cluster = "Tumor tissue"
no.markers = 30

# perturbed genes & metabolite
pdown.metabolite = c("LGALS1")
pdown.gene = c("LGALS3BP")

pup.metabolite = c("HMDB0000034")
pup.gene = c("HNRNPA2B1")

# controlled genes & metabolites for comparison
c.metabolite = c("MIF")
c.gene = c("CD74")

# perturb rate & noise level
rdown = 0.1
rup = 10
noise = 0.02

metabolite = c(pdown.metabolite, pup.metabolite, c.metabolite)
receptor = c(pdown.gene, pup.gene, c.gene)
tf = c("PCBP2", "YBX1", "HNRNPK")
target = c("MALAT1", "FBL", "NEAT1")
# target = seurat_RNA_markers$gene[seurat_RNA_markers$cluster == target.cluster][1:no.markers]

pdown.path = "LGALS1*LGALS3BP*PCBP2*MALAT1"
pup.path = "HMDB0000034*HNRNPA2B1*YBX1*FBL"
c.path = "MIF*CD74*HNRNPK*NEAT1"


n = length(unique(seurat_RNA@meta.data$cell_type))
M.initial = matrix(0, n, n)

rownames(M.initial) = unique(seurat_RNA@meta.data$cell_type) # sender
colnames(M.initial) = unique(seurat_RNA@meta.data$cell_type) # receiver

M.list = list(down = M.initial, up = M.initial, control = M.initial)

expression = c()
name = c()
condition = c()
iteration = c()

for (i in 1:round) {
  
  Data_RNA = seurat_RNA
  Data_MSI = seurat_MSI
  
  Data_RNA$condition = "control"
  Data_MSI$condition = "control"
  
  x = table(Data_RNA@meta.data$cell_type)
  x = x[unique(Data_RNA@meta.data$cell_type)]
  x = as.numeric(round(unname(x)/2))
  
  set.seed(NULL)
  index <- sampling:::strata(Data_RNA@meta.data, stratanames = "cell_type", size = x,
                             method = "srswor", description = TRUE)
  
  Data_MSI@meta.data$condition[index$ID_unit] = "perturbed"
  Data_RNA@meta.data$condition[index$ID_unit] = "perturbed"
  
  ##############################################################################
  # select cells (receptors)
  meta.data = Data_RNA@meta.data
  rownames(meta.data) = colnames(Data_RNA@assays$RNA@data)
  cell.use_down = rownames(meta.data)[meta.data$condition == "perturbed" & meta.data$cell_type == target.cluster]
  cell.use_up = rownames(meta.data)[meta.data$condition == "perturbed" & meta.data$cell_type == target.cluster]
  # change value
  Data_RNA@assays$RNA@data[pdown.gene, cell.use_down] = Data_RNA@assays$RNA@data[pdown.gene, cell.use_down]*rdown
  Data_RNA@assays$RNA@data[pup.gene, cell.use_up] = Data_RNA@assays$RNA@data[pup.gene, cell.use_up]*rup
  
  ##############################################################################
  # select cells for LS (metabolite)
  meta.data = Data_MSI@meta.data
  rownames(meta.data) = colnames(Data_MSI@assays$RNA@data)
  cell.use_up = rownames(meta.data)[meta.data$condition == "perturbed" & meta.data$cell_type == "Muscularis mucosa"]
  # change value
  Data_MSI@assays$RNA@data[pup.metabolite, cell.use_up] = Data_MSI@assays$RNA@data[pup.metabolite, cell.use_up]*rup
  
  ##############################################################################
  # select cells for LS (hormone)
  meta.data = Data_RNA@meta.data
  rownames(meta.data) = colnames(Data_RNA@assays$RNA@data)
  cell.use_down = rownames(meta.data)[meta.data$condition == "perturbed" & meta.data$cell_type == "Muscularis mucosa"]
  # change value
  Data_RNA@assays$RNA@data[pdown.metabolite, cell.use_down] = Data_RNA@assays$RNA@data[pdown.metabolite, cell.use_down]*rdown
  
  ##############################################################################
  # add noise
  a = dim(Data_RNA@assays$RNA@data)[1]
  b = dim(Data_RNA@assays$RNA@data)[2]
  # set.seed(1)
  set.seed(NULL)
  noise.M = matrix(round(rnorm(a*b, mean = 0, sd = 1), 2), a, b)
  noise.M = as( 1 + noise.M/max(noise.M)*noise , "dgCMatrix")
  Data_RNA@assays$RNA@data = Data_RNA@assays$RNA@data*noise.M
  
  # add noise
  a = dim(Data_MSI@assays$RNA@data)[1]
  b = dim(Data_MSI@assays$RNA@data)[2]
  # set.seed(2)
  set.seed(NULL)
  noise.M = matrix(round(rnorm(a*b, mean = 0, sd = 1), 2), a, b)
  noise.M = as( 1 + noise.M/max(noise.M)*noise , "dgCMatrix")
  Data_MSI@assays$RNA@data = Data_MSI@assays$RNA@data*noise.M
  
  ##############################################################################
  # Prepare input data sets
  Data_organ1 <- subset(Data_RNA, subset = organ == "organ1")
  Data_organ2 <- subset(Data_RNA, subset = organ == "organ2")
  
  Data_organ1@meta.data$cell_type <- fct_drop(Data_organ1@meta.data$cell_type)
  Data_organ2@meta.data$cell_type <- fct_drop(Data_organ2@meta.data$cell_type)
  
  Idents(Data_organ1) = Data_organ1@meta.data$cell_type
  Idents(Data_organ2) = Data_organ2@meta.data$cell_type
  
  data.list = list(data1 = Data_organ1@assays$RNA@data, data2 = Data_organ2@assays$RNA@data)
  idents.list = list(idents1 = Data_organ1@active.ident, idents2 = Data_organ2@active.ident)
  
  Idents(Data_organ1) = Data_organ1@meta.data$condition
  Idents(Data_organ2) = Data_organ2@meta.data$condition
  
  conditions.list = list(idents1 = Data_organ1@active.ident, idents2 = Data_organ2@active.ident)
  
  ##############################################################################
  CAOC = create_OrganChat(object = data.list, 
                          organs = c("organ1", "organ2"), 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = c("control", "perturbed"),
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
  
  ##############################################################################
  # Prepare the input scMETA data
  scMETA_organ1 <- subset(Data_MSI, subset = organ == "organ1")
  scMETA_organ2 <- subset(Data_MSI, subset = organ == "organ2")
  
  scMETA_organ1@meta.data$cell_type <- fct_drop(scMETA_organ1@meta.data$cell_type)
  scMETA_organ2@meta.data$cell_type <- fct_drop(scMETA_organ2@meta.data$cell_type)
  
  Idents(scMETA_organ1) = scMETA_organ1@meta.data$cell_type
  Idents(scMETA_organ2) = scMETA_organ2@meta.data$cell_type
  
  idents_organ1 = Idents(scMETA_organ1)
  idents_organ2 = Idents(scMETA_organ2)
  
  Idents(scMETA_organ1) = scMETA_organ1@meta.data$condition
  Idents(scMETA_organ2) = scMETA_organ2@meta.data$condition
  
  conditions.label_organ1 = Idents(scMETA_organ1)
  conditions.label_organ2 = Idents(scMETA_organ2)
  
  ##############################################################################
  CAOC = CA_cal_scMeta.bygroup(object = CAOC,
                               scMeta.data = scMETA_organ1@assays$RNA@data,
                               organ.name = "organ1",
                               idents = idents_organ1,
                               conditions.label = conditions.label_organ1,
                               mean_method = NULL,
                               type = "amount",
                               scale.max = 10)
  
  CAOC = CA_cal_scMeta.bygroup(object = CAOC,
                               scMeta.data = scMETA_organ2@assays$RNA@data,
                               organ.name = "organ2",
                               idents = idents_organ2,
                               conditions.label = conditions.label_organ2,
                               mean_method = NULL,
                               type = "amount",
                               scale.max = 10)
  
  CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                              DB = OrganChatDB,
                              mean_method = NULL,
                              scale.max = 10)
  
  CAOC = CA_net0_infer(object = CAOC,
                       DB = OrganChatDB, 
                       LS = metabolite, 
                       receptor = receptor, 
                       tf = tf,
                       target = target)
  
  CAOC = CA_net_analysis(object = CAOC,
                         K = 0.1, 
                         N = 1,
                         R = 5,
                         CA_cutoff_value = NULL,
                         CA_cutoff_chatP = NULL,
                         CA_cutoff_sd = NULL)
  
  CAOC = DEpath_table(object = CAOC,
                      Sender.group = NULL,
                      Receiver.group = NULL,
                      Direction = NULL,
                      p_cutoff = NULL,
                      sd_cutoff = NULL,
                      DI_cutoff = NULL,
                      top = NULL)
  
  ##############################################################################
  
  df = CAOC@DEpath
  df$ID_2 = paste0(df$Sender.group, "_", df$Receiver.group)
  
  df.down = df[df$Path == pdown.path, ]
  df.up = df[df$Path == pup.path, ]
  df.control = df[df$Path == c.path, ]
  
  df.list = list(down = df.down, up = df.up, control = df.control)
  
  for (j in 1:3) {
    df.output = df.list[[j]]
    M.select = M.initial
    for (k in 1:nrow(df.output)) {
      ind_row = which(rownames(M.select) == df.output$Sender.group[k])
      ind_col = which(colnames(M.select) == df.output$Receiver.group[k])
      M.select[ind_row, ind_col] = df.output$DI[k]
    }
    M.list[[j]] = M.list[[j]] + M.select
  }
  
  metabolite.exp_c = c(CAOC@LSdata$control$organ1[pdown.metabolite, ]$`Muscularis mucosa`,
                       CAOC@LSdata$control$organ1[pup.metabolite, ]$`Muscularis mucosa`,
                       CAOC@LSdata$control$organ1[c.metabolite, ]$`Muscularis mucosa`)
  
  metabolite.exp_p = c(CAOC@LSdata$perturbed$organ1[pdown.metabolite, ]$`Muscularis mucosa`,
                       CAOC@LSdata$perturbed$organ1[pup.metabolite, ]$`Muscularis mucosa`,
                       CAOC@LSdata$perturbed$organ1[c.metabolite, ]$`Muscularis mucosa`)
  
  receptor.exp_c = c(CAOC@DGdata$control$organ1[pdown.gene, ]$`Tumor tissue`,
                       CAOC@DGdata$control$organ1[pup.gene, ]$`Tumor tissue`,
                       CAOC@DGdata$control$organ1[c.gene, ]$`Tumor tissue`)
  
  receptor.exp_p = c(CAOC@DGdata$perturbed$organ1[pdown.gene, ]$`Tumor tissue`,
                       CAOC@DGdata$perturbed$organ1[pup.gene, ]$`Tumor tissue`,
                       CAOC@DGdata$perturbed$organ1[c.gene, ]$`Tumor tissue`)
  
  metabolite.exp = c(metabolite.exp_c, metabolite.exp_p)
  names.metabolite = rep(c(pdown.metabolite, pup.metabolite, c.metabolite), 2)
  
  receptor.exp = c(receptor.exp_c, receptor.exp_p)
  names.receptor = rep(c(pdown.gene, pup.gene, c.gene), 2)
  
  expression = c(expression, metabolite.exp, receptor.exp)
  name = c(name, names.metabolite, names.receptor)
  condition = c(condition, c(rep("control", 3), rep("perturbed", 3)), c(rep("control", 3), rep("perturbed", 3)))
  iteration = c(iteration, c(rep(i, 12)))
  
}

exp.outout = data.frame(expression = expression,
                        name = name,
                        condition = condition,
                        iteration = iteration)
```



```{r}
for (j in 1:3) {
  M.list[[j]] = M.list[[j]]/round
}
```


plot the heat map
```{r}
reorder.clusters = c("Blood-containing tissue", 
                     "Intestinal metaplasia", 
                     "Lamina propria", 
                     "Normal epithelium",
                     "Muscularis mucosa", 
                     "Peritumoral muscularis", 
                     "Tumor tissue")

upper.bound = max(max(M.list[[1]]), max(M.list[[2]]), max(M.list[[3]]))
lower.bound = min(min(M.list[[1]]), min(M.list[[2]]), min(M.list[[3]]))
bk <- c(seq(lower.bound, upper.bound, by = 0.05))

i = 3
df.plot = M.list[[i]]
df.plot = df.plot[reorder.clusters, reorder.clusters]

row_anno = data.frame(cluster = rownames(df.plot))
row_anno$cluster = factor(row_anno$cluster, levels = rownames(df.plot))
rownames(row_anno) = row_anno$cluster

col_anno = data.frame(cluster = colnames(df.plot))
rownames(col_anno) = col_anno$cluster
col_anno$cluster = factor(col_anno$cluster, levels = colnames(df.plot))

mycolors = brewer.pal(8, "Set1")[1:7]
names(mycolors) <- unique(col_anno$cluster)
mycolors <- list(cluster = mycolors)


# pdf( paste0(output.dir, "PerturbationHeatmap_", i, ".pdf"), width=12, height = 8)

pheatmap(df.plot,
         cluster_cols = F,
         cluster_rows = F,
         scale = "none",
         annotation_row = row_anno,
         annotation_col = col_anno,
         annotation_colors = mycolors,
         border_color = "white",
         color = colorRampPalette(c("navy", "white", "firebrick3"))(length(bk)),
         breaks = bk, 
         cellheight = 30, 
         cellwidth = 30,
         labels_col = c("", "", "", "", "", "", ""),
         labels_row = c("", "", "", "", "", "", ""))

# dev.off()
```

Box plot of the expression values
```{r}
# df.plot = exp.outout[exp.outout$name %in% c(pdown.metabolite, pup.metabolite), ]

df.plot = exp.outout
df.plot$name = factor(df.plot$name, 
                      levels = c(pdown.metabolite, pup.metabolite, c.metabolite, pdown.gene, pup.gene, c.gene))

p <- ggplot(df.plot, aes(x=name, y=expression, fill=condition)) + 
  geom_boxplot() +
  theme_bw() +
  facet_wrap(~name, scale="free", 
             labeller = labeller(name = c("HMDB0000191" = "Tumor tissue",
                                          "HMDB0000803" = "Tumor tissue",
                                          "HMDB0000131" = "Blood-containing tissue",
                                          "RPSA" = "Muscularis mucosa",
                                          "PIGR" = "Muscularis mucosa",
                                          "RACK1" = "Muscularis mucosa")))

p

# ggsave(p, filename=paste0(output.dir, "PerturbationExpression_Boxplot.pdf") )
```






