---
title: "MultiOrgan_Mouse_UCI_Validation_Liver_Adipose_Insulin_NewDB"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

```{r}
library(OrganChat)

library(readr)
library(forcats)
```

# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"    # your path to the ouput folder
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```


Load the Seurat object, which will be stored in a list
c("Liver", "Skin", "Adipose")
```{r}
organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

UCI_Data_list <- list()

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] = readRDS(paste0(data.path, "UCI_", organ.list[i], "_downsampled.rds"))
}

names(UCI_Data_list) = organ.list
```


################################################################################

# Select target genes
Select target genes
cluster markers of the Adipose cells in the "old_sensitive" condition
```{r}
Data.use.1 = subset(UCI_Data_list[["Adipose"]], 
                    subset = condition == "old_sensitive" ) 
 #                      Type %in% c("B cells", "Endothelial cells", "Mesenchymal progenitors", "Myeloid cells", "T cells"))
Data.use.1 <- SetIdent(Data.use.1, value = Data.use.1$Type)

# infer markers 
markers.Type <- FindAllMarkers(Data.use.1, only.pos = FALSE)

# the total number of targets will be ~5N
N = 30

markers.Type %>%
  group_by(cluster) %>%
  dplyr::arrange(abs(avg_log2FC)) %>%
  slice_head(n = N) %>%
  ungroup() -> top.markers

target = unique(top.markers$gene)

# write_csv(markers.Type, file = paste0(data.path, "Marker_Adipose_old_sensitive.csv"))
```



Setup organs & conditions
```{r}
# organs for validation
S.organ = "Liver"
R.organ = "Adipose"

# conditions for validation
conditions = c("old_sensitive", "old_resistant")
```


# CAOC analysis (OS vs. OR)

```{r, include=FALSE}
path = "~/Data/"

organs = c(S.organ, R.organ)

data.list = list()
idents.list = list()
conditions.list = list()

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  # select subset data of the two conditions
  Data.input_organ <- subset(UCI_Data_list[[organ.select]], subset = condition %in% conditions)
  Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
  Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
  
  data.list[[i]] = Data.input_organ@assays$RNA@data
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}

# Create OC object
CAOC = create_OrganChat(object = data.list, 
                        organs = organs, 
                        idents.list = idents.list,
                        ComparisonAnalysis = TRUE,
                        conditions = conditions,
                        conditions.list = conditions.list,
                        assay = NULL, 
                        do.sparse = T)

# Calculate the expression level using the scRNA-seq data
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)

# Prepare the metabolite flux data
organs = CAOC@organs

metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}

# Integrate metabolite data
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)

################################################################################
LS.names = c()
DG.names = c()

for (i in 1:length(conditions)) {

  LS.1 = CAOC@LSdata[[i]][[1]]
  LS.2 = CAOC@LSdata[[i]][[2]]

  DG.1 = CAOC@DGdata[[i]][[1]]
  DG.2 = CAOC@DGdata[[i]][[2]]

  LS.1$sum = apply(LS.1[ , 1:(ncol(LS.1)-1)], 1, sum)
  LS.2$sum = apply(LS.2[ , 1:(ncol(LS.2)-1)], 1, sum)
  DG.1$sum = apply(DG.1, 1, sum)
  DG.2$sum = apply(DG.2, 1, sum)

  LS.names = unique( c(LS.names, rownames(LS.1[LS.1$sum>0, ]), rownames(LS.2[LS.2$sum>0, ])) )
  DG.names = unique( c(DG.names, rownames(DG.1[DG.1$sum>0, ]), rownames(DG.2[DG.2$sum>0, ])) )
}
################################################################################

# Infer signaling paths
CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = LS.names, 
                     receptor = DG.names, 
                     tf = DG.names,
                     target = target)

# Analysis
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.1, 0.1, 0.1),
                       CA_cutoff_chatP = NULL,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)

# Infer DEpath
CAOC = DEpath_table(object = CAOC,
                    Sender.group = NULL,
                    Receiver.group = NULL,
                    Direction = NULL,
                    p_cutoff = NULL,
                    sd_cutoff = NULL,
                    DI_cutoff = NULL,
                    top = NULL)

# save the "object_list"
# saveRDS(CAOC, file = paste0(data.path, "Validation_Liver_to_Adipose_Top", N, ".rds") )
```

################################################################################

Load object
```{r}
Vali.Data = CAOC
```


Export the table
```{r}
Sender.organ = "Liver"
Receiver.organ = "Adipose"
Direction = "forward"

chatP.cutoff = 0.4

Results.Table = Vali.Data@DEpath[ Vali.Data@DEpath$Direction == "forward" &
                                    Vali.Data@DEpath$chatP_old_sensitive > chatP.cutoff, ]

markers.Type %>%
  group_by(cluster) %>%
  dplyr::arrange(abs(avg_log2FC)) %>%
  slice_head(n = 30) %>%
  ungroup() -> top.markers

Markers.Table = top.markers[ , c("cluster", "gene")]
Results.Table = inner_join(Results.Table, Markers.Table, join_by(Receiver.group == cluster, Target == gene))
```


Add LS expression to the table
```{r}
Sender.groups = unique(Results.Table$Sender.group)
LS.list = unique(Results.Table$LS)

LS.exp.1 = Vali.Data@LSdata$old_sensitive$Liver[LS.list, Sender.groups]
LS.exp.2 = Vali.Data@LSdata$old_resistant$Liver[LS.list, Sender.groups]

LS.exp.list.1 = list()
LS.exp.list.2 = list()
for (i in 1:length(Sender.groups)) {
  LS.exp.list.1[[i]] = data.frame(LS = rownames(LS.exp.1), LS.exp.1 = LS.exp.1[ , Sender.groups[i]], Sender.group = Sender.groups[i])
  LS.exp.list.2[[i]] = data.frame(LS = rownames(LS.exp.2), LS.exp.2 = LS.exp.2[ , Sender.groups[i]], Sender.group = Sender.groups[i])
}

LS.exp.1 = rbindlist(LS.exp.list.1)
LS.exp.2 = rbindlist(LS.exp.list.2)

Results.Table = left_join(Results.Table, LS.exp.1, join_by(LS, Sender.group))
Results.Table = left_join(Results.Table, LS.exp.2, join_by(LS, Sender.group))
```


Add Target expression
```{r}
Receiver.groups = unique(Results.Table$Receiver.group)
Target.list = unique(Results.Table$Target)

Target.exp.1 = Vali.Data@DGdata$old_sensitive$Adipose[Target.list, Receiver.groups]
Target.exp.2 = Vali.Data@DGdata$old_resistant$Adipose[Target.list, Receiver.groups]

Target.exp.list.1 = list()
Target.exp.list.2 = list()
for (i in 1:length(Receiver.groups)) {
  Target.exp.list.1[[i]] = data.frame(Target = rownames(Target.exp.1), 
                                      Target.exp.1 = Target.exp.1[ , Receiver.groups[i]], 
                                      Receiver.group = Receiver.groups[i])
  Target.exp.list.2[[i]] = data.frame(Target = rownames(Target.exp.2), 
                                      Target.exp.2 = Target.exp.2[ , Receiver.groups[i]], 
                                      Receiver.group = Receiver.groups[i])
}

Target.exp.1 = rbindlist(Target.exp.list.1)
Target.exp.2 = rbindlist(Target.exp.list.2)

Results.Table = left_join(Results.Table, Target.exp.1, join_by(Target, Receiver.group))
Results.Table = left_join(Results.Table, Target.exp.2, join_by(Target, Receiver.group))
```



For each target, find the ligands & the total signal flow
```{r}
label = c("-1", "-0.5", "-0.1", "0.1", "0.5", "1")
df.lilst = list()
for (i in 1:length(Receiver.groups)) {
  df = Results.Table[Results.Table$Receiver.group == Receiver.groups[i], ]

  df$chatP_old_sensitive.score = df$chatP_old_sensitive

  df$LS.change.score = log2((df$LS.exp.1 + 0.0001)/(df$LS.exp.2+0.0001)) # adding 0.0001 to avoid divition over zero
  
  target.list = unique(df$Target)
  
  LS.change = c()
  LS.change.score = c()
  Target.exp.1 = c()
  Target.exp.2 = c()
  for (j in 1:length(target.list)) {
    df.target = df[df$Target == target.list[[j]], ]
    
    LS.change.score = c(LS.change.score, sum(df.target$LS.change.score*df.target$chatP_old_sensitive.score)/nrow(df.target))
    
    Target.exp.1 = c( Target.exp.1, unique(df.target$Target.exp.1) )
    Target.exp.2 = c( Target.exp.2, unique(df.target$Target.exp.2) )
  }
  df.lilst[[i]] = data.frame(Target = target.list, LS.change.score = LS.change.score, 
                      Receiver.group = Receiver.groups[i],
                      Target.exp.1 = Target.exp.1, Target.exp.2 = Target.exp.2)
}

df_pair = rbindlist(df.lilst)
df_pair$score = (df_pair$LS.change.score)*(df_pair$Target.exp.1 - df_pair$Target.exp.2)

length(df_pair$score[df_pair$score>0])/nrow(df_pair)
df_pair_2 = inner_join(df_pair, top.markers, join_by(Target == gene, Receiver.group == cluster))
```


# Visualization

```{r}
library(plotrix)
library(pheatmap)
```

## Pie plot

Pie plot: overview
```{r}
Hit = nrow(df_pair_2[df_pair_2$score > 0, ])
All = nrow(df_pair_2)
Miss = All - Hit

slices <- c(Hit, Miss)
lbls <- c( paste0("Hit: ", Hit), paste0("Miss: ", Miss) )

pie3D(slices, labels = lbls, 
      explode = 0, height = 0.1,
      labelcex = 0.75,
      col = c("#F7921E", "#D2EEEA"),
      # col = hcl.colors(length(lbls), "Set 2"),
      border = "white", 
      main="Targets in Adipose" )
```


Pie plot -- each cell type
```{r}
Cell_Type = unique(df_pair_2$Receiver.group)

for (i in 1:length(Cell_Type)) {
  Hit = nrow(df_pair_2[df_pair_2$score > 0 & df_pair_2$Receiver.group == Cell_Type[i], ])
  All = nrow(df_pair_2[df_pair_2$Receiver.group == Cell_Type[i], ])
  Miss = All - Hit
  
  slices <- c(Hit, Miss)
  lbls <- c( paste0("Hit: ", Hit), paste0("Miss: ", Miss) )
  
  if ( Miss == 0){
    pie3D(Hit, labels = lbls[1], 
          explode = 0, height = 0.1,
          labelcex = 0.75,
          col = c("#F7921E"),
          border = "white", 
          main= paste0("Targets in Adipose, ", Cell_Type[i]) )
  }else{
    pie3D(slices, labels = lbls, 
          explode = 0, height = 0.1,
          labelcex = 0.75,
          col = c("#F7921E", "#D2EEEA"),
          border = "white", 
          main= paste0("Targets in Adipose, ", Cell_Type[i]) )
  }
}
```


Pie plot -- Diabetes-related targets
```{r}
dia_genes = c("Dctn2", "Rtn3", "Cox6a1", "Asah1", "Larp4b", "Ndufb2", "Sppl3", "Psmb4", "Luc7l", "Anxa5", "Tpst2", "Vapb", "Txndc17", "Abhd17a", "Ppia", "Ube2d3", "Ubb")

Hit = nrow(df_pair_2[df_pair_2$score > 0 & df_pair_2$Target %in% dia_genes, ])
All = nrow(df_pair_2[df_pair_2$Target %in% dia_genes, ])
Miss = All - Hit

slices <- c(Hit, Miss)
lbls <- c( paste0("Hit: ", Hit), paste0("Miss: ", Miss) )

pie3D(slices, labels = lbls, 
      explode = 0, height = 0.1,
      labelcex = 0.75,
      col = c("#F7921E", "#D2EEEA"),
      # col = hcl.colors(length(lbls), "Set 2"),
      border = "white", 
      main="Diabetes-related Targets" )
```


## Chorddiagram

OS_vs_OR, Liver -> Adipose
```{r}
object = Vali.Data

object@idents.list$Liver = object@idents.list$Liver[ object@idents.list$Liver %in% c("EC", "zone 1", "zone 2", "zone 3")]
object@idents.list$Liver = fct_drop(object@idents.list$Liver)

# OS_vs_OR, Liver -> Adipose, total number of nonpeptide hormone-driven LS-T pathways with communication probability > 0.7
CAOC_chorddiagram(object = object,
                  dir = "forward",
                  category = "hormone_nonpeptide",
                  style = "total.counts",
                  chatP_cutoff = 0.7)

# OS_vs_OR, Liver -> Adipose, total number of peptide hormone-driven LS-T pathways with communication probability > 0.7
CAOC_chorddiagram(object = object,
                  dir = "forward",
                  category = "hormone_peptide",
                  style = "total.counts",
                  chatP_cutoff = 0.7)

# OS_vs_OR, Liver -> Adipose, total number of cytokine-driven LS-T pathways with communication probability > 0.7
CAOC_chorddiagram(object = object,
                  dir = "forward",
                  category = "cytokines",
                  style = "total.counts",
                  chatP_cutoff = 0.7,
                  big.gap = 20,
                  directional = 1,  
                  grid.col = NULL)

# OS_vs_OR, Liver -> Adipose, total number of metabolite-driven LS-T pathways with communication probability > 0.7
CAOC_chorddiagram(object = object,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.7)
```


## LS-T pathways activating the diabetes-related targets (dia_genes)

OR, Liver (zone 2) -> Adipose (Mesenchymal progenitors), targeting dia_genes, communication probability > 0.3
```{r}
df_Hit = df_pair_2[df_pair_2$score>0 & df_pair_2$Receiver.group == "Mesenchymal progenitors", ]

df.plot = Vali.Data@net$old_resistant$forward$`zone 2_to_Mesenchymal progenitors`
df.plot = df.plot[df.plot$Target %in% dia_genes &
                    df.plot$chatP > 0.3, ]

p <- OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)

p 
```


Input for GO analysis is the targets for: OR, Liver (zone 2) -> Adipose (Mesenchymal progenitors), communication probability > 0.7
```{r}
df.plot = Vali.Data@net$old_resistant$forward$`zone 2_to_Mesenchymal progenitors`
df.plot = df.plot[ df.plot$chatP > 0.7, ]

x = OC_GOanalysis(df = df.plot,
                  LS = NULL,
                  layer = "Target")

GOanalysis_scatterplot(df = x$result,
                       n = 10,
                       size=6)
```



## SL Figures for main figure 3

OR, Liver (EC) -> Adipose (Mesenchymal progenitors), targets: dia_genes
```{r}
df.plot = Vali.Data@net$old_resistant$forward$`EC_to_Mesenchymal progenitors`
df.plot = df.plot[df.plot$Target %in% dia_genes, ]

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


OS, Liver (zone 3) -> Adipose (Endothelial cells), targets: dia_genes
```{r}
df.plot = Vali.Data@net$old_sensitive$forward$`zone 3_to_Endothelial cells`
df.plot = df.plot[df.plot$Target %in% dia_genes, ]

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


Bubble heat map: Liver -> Adipose, cytokine-driven LS-T pathways
```{r}
CAOC_bubbleheatmap(object = Vali.Data,
                   dir = "forward",
                   chatP_cutoff = 0.1,
                   category = "cytokines",
                   size = "total.counts",
                   color = "ave.weight")

```


Bubble heat map: Liver -> Adipose
```{r}
CAOC_bubbleheatmap(object = Vali.Data,
                   dir = "forward",
                   chatP_cutoff = 0.1,
                   category = "All",
                   size = "total.counts",
                   color = "ave.weight")
```





