---
title: "MultiOrgan_Mouse_UCI_MOOC_T2D"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

```{r}
library(OrganChat)

library(readr)
library(forcats)
```

# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"    # your path to the ouput folder
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```



Load the Seurat object
c("Liver", "Skin", "Adipose")
```{r}
organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

UCI_Data_list <- list()

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] = readRDS(paste0(data.path, "UCI_", organ.list[i], "_downsampled.rds"))
}

names(UCI_Data_list) = organ.list
```


# Multi-organ OrganChat analysis


Insulin-resistance–associated human genes from Gene Set Enrichment Analysis (GSEA)
```{r}
T2D.list = c("ZMPSTE24", "MICU1", "AGPAT2", "CEL", "IGF2BP2", "SDCCAG8", "ADCY3", "IFT27", "CLCNKB", "TTC8", "BBS5", "SCLT1", 
 "CFAP418", "CYP19A1", "DBH", "BBS12", "SLC30A8", "ERCC6", "AKT2", "LEMD2", "TRIM32", "CNOT1", "PHLDB1", "FOS", 
 "PTF1A", "APPL1", "IFT172", "GATA6", "GCK", "BSCL2", "BBS9", "GPD2", "CAVIN1", "NSMCE2", "GRB10", "HMGA1", 
 "HNF4A", "HSD11B1", "ZFP57", "IGF1", "IGFALS", "IL6", "INS", "INSR", "PDX1", "IRF4", "IRS1", "KCNJ11", "LEP", 
 "LEPR", "LIPC", "LIPE", "LMNA", "MTNR1B", "NEUROD1", "NPHP1", "SCAPER", "PAX4", "WDPCP", "ENPP1", "PIK3R1", 
 "PLAGL1", "PLIN1", "PMM2", "POLD1", "LZTFL1", "PPARG", "MKS1", "PPP1R3A", "BBS7", "RETN", "HYMAI", "PTPN1", 
 "BBS1", "BBS2", "BBS4", "CIDEC", "BLK", "BLM", "SLC2A2", "SLC5A2", "SLC12A3", "STAT3", "ABCC8", "HNF1A", 
 "HNF1B", "TCF7L2", "WFS1", "WRN", "XRCC4", "ALMS1", "CCDC28B", "BBS10", "DCAF17", "IFT74", "CEP290", "MKKS", 
 "ARL6", "KLF11", "LMNB2", "CEP19", "CAV1", "IRS2", "BBIP1", "EIF2AK3", "MAPK8IP1", "MFN2")

T2D.list_mouse = gorth(query = T2D.list, source_organism = "hsapiens", target_organism = "mmusculus", numeric_ns = "")
T2D.genes = unique(T2D.list_mouse$ortholog_name)
```


Should perform the analysis for YS vs. OS, YS vs. OR, respectively.
You may also download the saved OrganChat objects from Zeonodo.

Select target genes
```{r}
# conditions = c("young", "old_sensitive") # young: YS
conditions = c("young", "old_resistant")
organs = names(UCI_Data_list)

target = T2D.genes
```


Create data inputs
```{r}
data.list = list()
idents.list = list()

for (i in 1:length(UCI_Data_list)){
  organ.select = organs[i]
  # select subset data of the two conditions
  Data.input_organ <- subset(UCI_Data_list[[i]], subset = condition %in% conditions)
  Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
  Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
  
  data.list[[i]] = Data.input_organ@assays$RNA@data
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}
```


Create OC object
```{r}
MOOC = create_OrganChat(object = data.list, 
                        organs = organs,
                        idents.list = idents.list, 
                        ComparisonAnalysis = TRUE,
                        conditions = conditions,
                        conditions.list = conditions.list,
                        assay = NULL, 
                        do.sparse = T)
```


Integrate the scRNA-seq data
```{r}
MOOC = MO_cal_scRNA.bygroup(object = MOOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```


save the objects (also available on Zenodo)
```{r}
# saveRDS(MOOC, file = paste0(output.dir, "Validation_MOOC_T2D_young_olds.rds"))
saveRDS(MOOC, file = paste0(output.dir, "Validation_MOOC_T2D_young_oldr.rds"))
```


Prepare the metabolite flux data
```{r, include=FALSE}
organs = MOOC@organs

metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

Integrate the flux data
```{r}
MOOC <- MO_merge_metabolite.bygroup(object = MOOC,
                                    metabolitedata.list.condition1 = metalist.1,
                                    metabolitedata.list.condition2 = metalist.2,
                                    type = "flux",
                                    scale.max = 10)
```


Pairwise analysis with 105 targets (~8.11hours)
You may also download the saved results from Zenodo.
```{r}

start.time <- Sys.time()

MOOC.net <- MO_pairwise_analysis(object = MOOC,
                             DB = OrganChatDB, 
                             LS = NULL, 
                             receptor = NULL, 
                             tf = NULL,
                             target = target,
                             K = 0.1, 
                             N = 1,
                             R = 100,
                             CI = 0.95,
                             CA_cutoff_value = c(0, 0.3, 0.3, 0.3),
                             CA_cutoff_chatP = 0.3,
                             CA_cutoff_sd = NULL,
                             CA_cutoff_CI = 0)

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```


save the results (also available on Zenodo)
```{r}
# saveRDS(MOOC.net, file = paste0(output.dir, "Validation_MOOC_net_T2D_young_olds.rds"))
saveRDS(MOOC.net, file = paste0(output.dir, "Validation_MOOC_net_T2D_young_oldr.rds"))
```


# Summarize the analysis results

Load the saved MOOC results
```{r}
MOOC.1 = readRDS(paste0(data.path, "Validation_MOOC_T2D_young_olds.rds"))
MOOC.2 = readRDS(paste0(data.path, "Validation_MOOC_T2D_young_oldr.rds"))

MOOC.net.1 = readRDS(paste0(data.path, "Validation_MOOC_net_T2D_young_olds.rds"))
MOOC.net.2 = readRDS(paste0(data.path, "Validation_MOOC_net_T2D_young_oldr.rds"))
```


## Communication to Liver

```{r}
MOOC.net.1[[4]] # stores all organ-organ pairs

DE.table.list = list()
for (k in 1:2) {

  organs = MOOC.net.1[[4]][ , k]
  conditions = c("young", "old_sensitive")
  
  data.list = list()
  idents.list = list()
  conditions.list = list()
  
  for (i in 1:length(organs)){
    organ.select = organs[i]
    # select subset data of the two conditions
    Data.input_organ <- subset(UCI_Data_list[[organ.select]], subset = condition %in% conditions)
    Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
    Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
    
    data.list[[i]] = Data.input_organ@assays$RNA@data
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$Type
    idents.list[[i]] = Data.input_organ@active.ident
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$condition
    conditions.list[[i]] = Data.input_organ@active.ident
  }
  
  OC_1 = create_OrganChat(object = data.list, organs = organs, idents.list = idents.list, ComparisonAnalysis = TRUE,
                          conditions = conditions, conditions.list = conditions.list, assay = NULL, do.sparse = T)
  
  ################################################################################
  
  organs = MOOC.net.2[[4]][ , k]
  conditions = c("young", "old_resistant")
  
  data.list = list()
  idents.list = list()
  conditions.list = list()
  
  for (i in 1:length(organs)){
    organ.select = organs[i]
    # select subset data of the two conditions
    Data.input_organ <- subset(UCI_Data_list[[organ.select]], subset = condition %in% conditions)
    Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
    Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
    
    data.list[[i]] = Data.input_organ@assays$RNA@data
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$Type
    idents.list[[i]] = Data.input_organ@active.ident
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$condition
    conditions.list[[i]] = Data.input_organ@active.ident
  }
  
  OC_2 = create_OrganChat(object = data.list, organs = organs, idents.list = idents.list, ComparisonAnalysis = TRUE,
                          conditions = conditions, conditions.list = conditions.list, assay = NULL, do.sparse = T)
  
  ################################################################################
  OC_1@net = MOOC.net.1[[k]]
  OC_1 = DEpath_table(object = OC_1,
                      Sender.group = NULL,
                      Receiver.group = NULL,
                      Direction = NULL,
                      p_cutoff = NULL,
                      sd_cutoff = NULL,
                      DI_cutoff = NULL,
                      top = NULL)
  
  OC_2@net = MOOC.net.2[[k]]
  OC_2 = DEpath_table(object = OC_2,
                      Sender.group = NULL,
                      Receiver.group = NULL,
                      Direction = NULL,
                      p_cutoff = NULL,
                      sd_cutoff = NULL,
                      DI_cutoff = NULL,
                      top = NULL)
  
  DEtable_1 = OC_1@DEpath
  DEtable_2 = OC_2@DEpath
  DEtable_merge = inner_join(DEtable_1, DEtable_2[ , c("Path_ID", 
                                                       "chatP_old_resistant", "bootstrap_sd_old_resistant", 
                                                       "log2FC", "DI")], join_by("Path_ID"))
  DEtable_merge$Organ1 = organs[1]
  DEtable_merge$Organ2 = organs[2]
  
  DE.table.list[[k]] = DEtable_merge
  
}
```


Summarize the results of Liver <- Adipose, Liver <- Skin, and Liver <- Liver
```{r}
df1 = DE.table.list[[1]][DE.table.list[[1]]$Direction == "backward", ]
df2 = DE.table.list[[2]][DE.table.list[[2]]$Direction == "backward", ]

df3 = rbind(DE.table.list[[1]][DE.table.list[[1]]$Direction == "self_organ1", ],
                     DE.table.list[[2]][DE.table.list[[2]]$Direction == "self_organ1", ])

x1 = aggregate(chatP_young ~ Target, df1, mean) 
x2 = aggregate(chatP_old_sensitive ~ Target, df1, mean) 
x3 = aggregate(chatP_old_resistant ~ Target, df1, mean) 

y1 = aggregate(chatP_young ~ Target, df2, mean) 
y2 = aggregate(chatP_old_sensitive ~ Target, df2, mean) 
y3 = aggregate(chatP_old_resistant ~ Target, df2, mean)

z1 = aggregate(chatP_young ~ Target, df3, mean) 
z2 = aggregate(chatP_old_sensitive ~ Target, df3, mean) 
z3 = aggregate(chatP_old_resistant ~ Target, df3, mean)

x_combined = inner_join(x1, inner_join(x2, x3, join_by(Target)) , join_by(Target))
y_combined = inner_join(y1, inner_join(y2, y3, join_by(Target)) , join_by(Target))
z_combined = inner_join(z1, inner_join(z2, z3, join_by(Target)) , join_by(Target))

xyz = rbind(x_combined, y_combined, z_combined)

w1 = aggregate(chatP_young ~ Target, xyz, mean) 
w2 = aggregate(chatP_old_sensitive ~ Target, xyz, mean) 
w3 = aggregate(chatP_old_resistant ~ Target, xyz, mean)

DE.condition_Liver = inner_join(w1, inner_join(w2, w3, join_by(Target)) , join_by(Target))
```


## Communication to Adipose

```{r}
DE.table.list = list()
for (k in 2:3) {

  organs = MOOC.net.1[[4]][ , k]
  conditions = c("young", "old_sensitive")
  
  data.list = list()
  idents.list = list()
  conditions.list = list()
  
  for (i in 1:length(organs)){
    organ.select = organs[i]
    # select subset data of the two conditions
    Data.input_organ <- subset(UCI_Data_list[[organ.select]], subset = condition %in% conditions)
    Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
    Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
    
    data.list[[i]] = Data.input_organ@assays$RNA@data
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$Type
    idents.list[[i]] = Data.input_organ@active.ident
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$condition
    conditions.list[[i]] = Data.input_organ@active.ident
  }
  
  OC_1 = create_OrganChat(object = data.list, organs = organs, idents.list = idents.list, ComparisonAnalysis = TRUE,
                          conditions = conditions, conditions.list = conditions.list, assay = NULL, do.sparse = T)
  
  ################################################################################
  
  organs = MOOC.net.2[[4]][ , k]
  conditions = c("young", "old_resistant")
  
  data.list = list()
  idents.list = list()
  conditions.list = list()
  
  for (i in 1:length(organs)){
    organ.select = organs[i]
    # select subset data of the two conditions
    Data.input_organ <- subset(UCI_Data_list[[organ.select]], subset = condition %in% conditions)
    Data.input_organ@meta.data$condition <- fct_drop(Data.input_organ@meta.data$condition)
    Data.input_organ@meta.data$Type <- fct_drop(Data.input_organ@meta.data$Type)
    
    data.list[[i]] = Data.input_organ@assays$RNA@data
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$Type
    idents.list[[i]] = Data.input_organ@active.ident
    
    Idents(Data.input_organ) = Data.input_organ@meta.data$condition
    conditions.list[[i]] = Data.input_organ@active.ident
  }
  
  OC_2 = create_OrganChat(object = data.list, organs = organs, idents.list = idents.list, ComparisonAnalysis = TRUE,
                          conditions = conditions, conditions.list = conditions.list, assay = NULL, do.sparse = T)
  
  ################################################################################
  OC_1@net = MOOC.net.1[[k]]
  OC_1 = DEpath_table(object = OC_1,
                      Sender.group = NULL,
                      Receiver.group = NULL,
                      Direction = NULL,
                      p_cutoff = NULL,
                      sd_cutoff = NULL,
                      DI_cutoff = NULL,
                      top = NULL)
  
  OC_2@net = MOOC.net.2[[k]]
  OC_2 = DEpath_table(object = OC_2,
                      Sender.group = NULL,
                      Receiver.group = NULL,
                      Direction = NULL,
                      p_cutoff = NULL,
                      sd_cutoff = NULL,
                      DI_cutoff = NULL,
                      top = NULL)
  
  DEtable_1 = OC_1@DEpath
  DEtable_2 = OC_2@DEpath
  DEtable_merge = inner_join(DEtable_1, DEtable_2[ , c("Path_ID", 
                                                       "chatP_old_resistant", "bootstrap_sd_old_resistant", 
                                                       "log2FC", "DI")], join_by("Path_ID"))
  DEtable_merge$Organ1 = organs[1]
  DEtable_merge$Organ2 = organs[2]
  
  DE.table.list[[k-1]] = DEtable_merge
  
}
```


Summarize the results of Liver -> Adipose, Skin -> Adipose, and Adipose -> Adipose
```{r}
df1 = DE.table.list[[1]][DE.table.list[[1]]$Direction == "forward", ]
df2 = DE.table.list[[2]][DE.table.list[[2]]$Direction == "forward", ]

df3 = rbind(DE.table.list[[1]][DE.table.list[[1]]$Direction == "self_organ2", ],
                     DE.table.list[[2]][DE.table.list[[2]]$Direction == "self_organ2", ])

x1 = aggregate(chatP_young ~ Target, df1, mean) 
x2 = aggregate(chatP_old_sensitive ~ Target, df1, mean) 
x3 = aggregate(chatP_old_resistant ~ Target, df1, mean) 

y1 = aggregate(chatP_young ~ Target, df2, mean) 
y2 = aggregate(chatP_old_sensitive ~ Target, df2, mean) 
y3 = aggregate(chatP_old_resistant ~ Target, df2, mean)

z1 = aggregate(chatP_young ~ Target, df3, mean) 
z2 = aggregate(chatP_old_sensitive ~ Target, df3, mean) 
z3 = aggregate(chatP_old_resistant ~ Target, df3, mean)

x_combined = inner_join(x1, inner_join(x2, x3, join_by(Target)) , join_by(Target))
y_combined = inner_join(y1, inner_join(y2, y3, join_by(Target)) , join_by(Target))
z_combined = inner_join(z1, inner_join(z2, z3, join_by(Target)) , join_by(Target))

xyz = rbind(x_combined, y_combined, z_combined)

w1 = aggregate(chatP_young ~ Target, xyz, mean) 
w2 = aggregate(chatP_old_sensitive ~ Target, xyz, mean) 
w3 = aggregate(chatP_old_resistant ~ Target, xyz, mean)

DE.condition_Adipose = inner_join(w1, inner_join(w2, w3, join_by(Target)) , join_by(Target))
```


# Visualization

## T2D genes activation plot

For communications towards liver
```{r}
data <- as.matrix(DE.condition_Liver[ , 2:4])
rownames(data) = DE.condition_Liver$Target

pheatmap(data, scale = "row",
         cluster_rows = FALSE, cluster_cols = FALSE, 
         color = colorRampPalette(rev(brewer.pal(3, "Spectral")))(200),
         legend_breaks = c(-1, 0, 1),
         legend_labels = c("Low", "Medium", "High"),
         cellheight = 20, cellwidth = 20)
```



Validation via the data
```{r}
Target.exp.1 = MOOC.1@DGdata$young$Liver[DE.condition_Liver$Target , ]
Target.exp.2 = MOOC.1@DGdata$old_sensitive$Liver[DE.condition_Liver$Target , ]
Target.exp.3 = MOOC.2@DGdata$old_resistant$Liver[DE.condition_Liver$Target , ]

x = data.frame(Target.1 = apply(Target.exp.1, 1, mean), 
               Target.2 = apply(Target.exp.2, 1, mean), 
               Target.3 = apply(Target.exp.3, 1, mean))

data <- as.matrix(x)
rownames(data) = DE.condition_Liver$Target

pheatmap(data, scale = "row",
         cluster_rows = FALSE, cluster_cols = FALSE, 
         color = colorRampPalette(rev(brewer.pal(3, "RdBu")))(200),
         legend_breaks = c(-1, 0, 1),
         legend_labels = c("Low", "Medium", "High"),
         cellheight = 20, cellwidth = 20)
```


For communications towards adipose
```{r}
data <- as.matrix(DE.condition_Adipose[ , 2:4])
rownames(data) = DE.condition_Adipose$Target

pheatmap(data, scale = "row",
         cluster_rows = FALSE, cluster_cols = FALSE, 
         color = colorRampPalette(rev(brewer.pal(3, "Spectral")))(200),
         legend_breaks = c(-1, 0, 1),
         legend_labels = c("Low", "Medium", "High"),
         cellheight = 20, cellwidth = 20)
```



Validation via the data
```{r}
Target.exp.1 = MOOC.1@DGdata$young$Adipose[DE.condition_Adipose$Target , ]
Target.exp.2 = MOOC.1@DGdata$old_sensitive$Adipose[DE.condition_Adipose$Target , ]
Target.exp.3 = MOOC.2@DGdata$old_resistant$Adipose[DE.condition_Adipose$Target , ]

x = data.frame(Target.1 = apply(Target.exp.1, 1, mean), 
               Target.2 = apply(Target.exp.2, 1, mean), 
               Target.3 = apply(Target.exp.3, 1, mean))

data <- as.matrix(x)
rownames(data) = DE.condition_Adipose$Target

pheatmap(data, scale = "row",
         cluster_rows = FALSE, cluster_cols = FALSE, 
         color = colorRampPalette(rev(brewer.pal(3, "RdBu")))(200),
         legend_breaks = c(-1, 0, 1),
         legend_labels = c("Low", "Medium", "High"),
         cellheight = 20, cellwidth = 20)
```


## Visualize the MOOC analysis results

Here we use peptide hormone-driven communications as an example.

Circle plot showing the total number of the peptide hormone-driven communications with probability > 0.7, YS vs OS.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC.1,
                                MO.net.list = MOOC.net.1,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.7)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts",
               color.platte = brewer.pal(8, "Set2"),
               scale.edge.width = 10,
               scale.vertex.size = 30,
               vertex.frame.color = "white",
               vertex.label.color="black",
               vertex.label.dist = 3,
               edge.arrow.size = 0.6,
               edge.curved = 0.3,
               margin = 0.2,
               vertex.max = "condition1",
               edge.max = "condition1")
```


Circle plot showing the total number of the peptide hormone-driven communications with probability > 0.7, YS vs OR.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC.2,
                                MO.net.list = MOOC.net.2,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.7)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts",
               color.platte = brewer.pal(8, "Set2"),
               scale.edge.width = 10,
               scale.vertex.size = 30,
               vertex.frame.color = "white",
               vertex.label.color="black",
               vertex.label.dist = 3,
               edge.arrow.size = 0.6,
               edge.curved = 0.3,
               margin = 0.2,
               vertex.max = "condition1",
               edge.max = "condition1")
```


Circle plot showing the total strength (total communication probability) of the peptide hormone-driven communications with probability > 0.7, YS vs OS.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC.1,
                                MO.net.list = MOOC.net.1,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.7)

MO_networkplot(network.input = MOOC.plot,
               style = "total.chatP",
               color.platte = brewer.pal(8, "Set2"),
               scale.edge.width = 10,
               scale.vertex.size = 30,
               vertex.frame.color = "white",
               vertex.label.color="black",
               vertex.label.dist = 3,
               edge.arrow.size = 0.6,
               edge.curved = 0.3,
               margin = 0.2,
               vertex.max = "condition1",
               edge.max = "condition1")
```

Circle plot showing the total strength (total communication probability) of the peptide hormone-driven communications with probability > 0.7, YS vs OR.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC.2,
                                MO.net.list = MOOC.net.2,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.7)

MO_networkplot(network.input = MOOC.plot,
               style = "total.chatP",
               color.platte = brewer.pal(8, "Set2"),
               scale.edge.width = 10,
               scale.vertex.size = 30,
               vertex.frame.color = "white",
               vertex.label.color="black",
               vertex.label.dist = 3,
               edge.arrow.size = 0.6,
               edge.curved = 0.3,
               margin = 0.2,
               vertex.max = "condition1",
               edge.max = "condition1")
```



## Pathway plot

### For communication between Liver & Adipose (YS vs. OR)

Built the OC object
```{r}
organs = c("Liver", "Adipose")
OC.2 = MOOC.2
OC.2@organs = OC.2@organs[c(1,3)]

OC.2@data.list = OC.2@data.list[organs]
OC.2@idents.list = OC.2@idents.list[organs]
OC.2@conditions.list = OC.2@conditions.list[organs]

OC.2@idents.list$Liver = fct_drop(OC.2@idents.list$Liver)

OC.2@LSdata$young = OC.2@LSdata$young[organs]
OC.2@LSdata$old_resistant = OC.2@LSdata$old_resistant[organs]
OC.2@DGdata$young = OC.2@DGdata$young[organs]
OC.2@DGdata$old_resistant = OC.2@DGdata$old_resistant[organs]

OC.2@net = MOOC.net.2[[2]]
```


Here we use metabolite-driven communications as an example.

Chor diagram: Liver <- Adipose
```{r}
OC_chorddiagram(object = OC.2,
                net = OC.2@net$old_resistant$backward, # a list of sig network of one direction
                dir = "backward",
                category = "metabolite",
                style = "total.chatP",)
```


River plot: Liver (zone 3) <- Adipose (Mesenchymal progenitors), OR condition
```{r}
df.plot = OC.2@net$old_resistant$backward$`Mesenchymal progenitors_to_zone 3`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "metabolite",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```



### For communication between Skin & Adipose (YS vs. OS)

Built the OC object
```{r}
organs = c("Skin", "Adipose")
OC.1 = MOOC.1
OC.1@organs = OC.1@organs[c(2,3)]

OC.1@data.list = OC.1@data.list[organs]
OC.1@idents.list = OC.1@idents.list[organs]
OC.1@conditions.list = OC.1@conditions.list[organs]

OC.1@idents.list$Skin = fct_drop(OC.1@idents.list$Skin)
OC.1@idents.list$Adipose = fct_drop(OC.1@idents.list$Adipose)

OC.1@LSdata$young = OC.1@LSdata$young[organs]
OC.1@LSdata$old_resistant = OC.1@LSdata$old_resistant[organs]
OC.1@DGdata$young = OC.1@DGdata$young[organs]
OC.1@DGdata$old_resistant = OC.1@DGdata$old_resistant[organs]

OC.1@net = MOOC.net.1[[3]]
```


Here we use peptide hormone-driven communications as an example.

Chord diagram: Skin -> Adipose
```{r}
OC_chorddiagram(object = OC.1,
                net = OC.1@net$young$forward, # a list of sig network of one direction
                dir = "forward",
                category = "hormone_peptide",
                style = "total.chatP")
```



River plot: Skin (Sebaceous gland) -> Adipose (Mesenchymal progenitors), YS condition
```{r}
df.plot = OC.1@net$young$forward$`Sebaceous gland_to_Mesenchymal progenitors`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "hormone_peptide",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


## Extended analysis figures

```{r}
OC_chorddiagram(object = OC.2,
                net = OC.2@net$old_resistant$backward, # a list of sig network of one direction
                dir = "backward",
                category = "metabolite",
                style = "total.chatP")
```


```{r}
df.plot = OC.2@net$old_resistant$backward$`T cells_to_zone 3`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "metabolite",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```



```{r}
OC_chorddiagram(object = OC.2,
                net = OC.2@net$old_resistant$backward, # a list of sig network of one direction
                dir = "backward",
                category = "hormone_peptide",
                style = "total.chatP")
```



```{r}
df.plot = OC.2@net$old_resistant$backward$`Mesenchymal progenitors_to_zone 3`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "metabolite",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```





```{r}
df.plot = Vali.Data@DEpath[Vali.Data@DEpath$Direction == "forward" &
                            Vali.Data@DEpath$Sender.group == "zone 3" &
                             Vali.Data@DEpath$Receiver.group == "Endothelial cells" &
                             Vali.Data@DEpath$Path %in% p@data$Path, ]

df.plot = df.plot[abs(df.plot$DI) > 0.05, ]

CAOC_RI_barplot(df = df.plot,
                n = 10,
                axis.text.size = 50)
```
