---
title: "MultiOrgan_Mouse_UCI_DataProcessingMetaboliteAnalysis"
author: "Changhan"
date: "2026-04-26"
output: html_document
---

Data processing includes: (1) down sampling; (2) humen gene convertion for flux data analysis.

The raw and processed liver, skin and adipose scRNA-seq data is deposited at Gene Expression Omnibus (GEO): GSE317326 (https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE317326). The dataset will be publicly available upon publication.

The required data to run the analysis can be downloaded from: https://doi.org/10.5281/zenodo.19042679.

```{r}
library(Seurat)

library(scCustomize)
library(sceasy)
```


# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse/"    # your path to the ouput folder
```


Load and scale the Seurat objects for three organs
```{r}
UCI_Data_list = list()

organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] <- readRDS(paste0(data.path, "UCI_", organ.list[i], ".rds"))
}

names(UCI_Data_list) = organ.list
```


Construct a list of condition-specific data
```{r}
UCI_conditionData_list <- list()

for (i in 1:length(organ.list)) {
  df.list = list(old_resistant = list(), old_sensitive = list(), young = list())
  
  seurat.object = UCI_Data_list[[organ.list[i]]]
  
  df.list[["old_resistant"]] = subset(seurat.object, subset = condition == "old_resistant")
  df.list[["old_sensitive"]] = subset(seurat.object, subset = condition == "old_sensitive")
  df.list[["young"]] = subset(seurat.object, subset = condition == "young")
  
  UCI_conditionData_list[[i]] = df.list
}
names(UCI_conditionData_list) = organ.list
```


```{r}
for (i in 1:length(UCI_conditionData_list)) {

  print(table(UCI_conditionData_list[[i]]$old_resistant$Type))
  print(table(UCI_conditionData_list[[i]]$old_sensitive$Type))
  print(table(UCI_conditionData_list[[i]]$young$Type))
}
```



For computation efficiency, we randomly selected 50% of the cells in clusters with >200 cells. 
For quality control purpose, we dropped the clusters with <50 cells.
```{r}
UCI_subset_conditionData_list = UCI_conditionData_list

downsample.rate = 0.5
mincells = 200
cutoff_population = 50

for (i in 1:length(UCI_conditionData_list)) {
  for (j in 1:length(condition.list)) {
    # select the seurat object
    datause <- UCI_conditionData_list[[i]][[j]]
    metause <- UCI_conditionData_list[[i]][[j]]@meta.data
    # select clusters with >200 cells
    cluster = names(table(datause$Type)[table(datause$Type)>mincells])
    # down-sampling
    cellbarcodes = colnames(datause@assays$RNA@data)
    rownames(metause) = cellbarcodes
    remove_cells <- c()
    for (k in 1:length(cluster)) {
      # cell barcodes of the down-sampled cluster
      metause_downsample = metause[metause$Type == cluster[k], ]
      # cells that need to be removed
     cellbarcodes_downsample = rownames( metause_downsample[sample( nrow(metause_downsample), floor(nrow(metause_downsample)*(1-downsample.rate)) ), ] )
      # barcodes of the cells to be removed
      remove_cells <- c(remove_cells, cellbarcodes_downsample)
    }
    cellbarcodes = cellbarcodes[!(cellbarcodes %in% remove_cells)]
    data.output = subset(datause, cells = cellbarcodes)
    # add cell type label
    data.output@meta.data$Type = fct_drop(data.output@meta.data$Type)
    # select clusters with population > cutoff value
    cluster_cutoff = names(table(data.output$Type)[table(data.output$Type)>cutoff_population])
    data.output = subset(data.output, Type %in% cluster_cutoff)
    data.output@meta.data$Type = fct_drop(data.output@meta.data$Type)
    # add condition label
    data.output@meta.data$condition = names(UCI_conditionData_list[[i]][j])
      
    UCI_subset_conditionData_list[[i]][[j]] = data.output
  }
}
```


Merge and save
```{r}
for (i in 1:length(UCI_subset_conditionData_list)) {
  merged_object <- Merge_Seurat_List(list_seurat = UCI_subset_conditionData_list[[i]])
  # saveRDS(merged_object, paste0(data.path, "UCI_", names(UCI_subset_conditionData_list[i]), "_downsampled.rds"))
}
```


# Convert genes to human gene symbols for flux data analysis

```{r}
library(gprofiler2)
```


Load the Seurat object
```{r}
organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

UCI_Data_list <- list()

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] = readRDS(paste0(data.path, "UCI_", organ.list[i], "_downsampled.rds"))
}

names(UCI_Data_list) = organ.list
```


```{r}
for (i in 1:length(UCI_Data_list)) {
  Data.input = UCI_Data_list[[i]]
  
  gene.input = rownames(Data.input@assays$RNA@counts)
  counts.input = Data.input@assays$RNA@counts
  meta.input = Data.input@meta.data
  
  convert.df = gorth(query = gene.input, 
                     source_organism = "mmusculus", target_organism = "hsapiens", numeric_ns = "ENTREZGENE_ACC")
  convert.df = data.frame(input = convert.df$input, output = convert.df$ortholog_name)
  
  # the count matrix
  df = as.data.frame(counts.input)
  # select the converted genes
  df$input = rownames(df)
  df = right_join(df, convert.df, join_by(input == input))
  df = df[!duplicated(df$output) & !is.na(df$output), ]
  rownames(df) = df$output
  
  # the new count matrix
  df = df[ , 1:(ncol(df)-2)]
  counts.new = as.matrix(df)
  
  # Create the new Seurat object (with converted genes)
  options(Seurat.object.assay.version = "v5")
  Data.output <- CreateSeuratObject(counts = counts.new, meta.data = meta.input)
  Data.output <- NormalizeData(Data.output)
  
  # saveRDS(Data.output, paste0(data.path, "UCI_", names(UCI_Data_list[i]), "_downsampled_humanconverted.rds"))
  
  UCI_Data_list[[i]] = Data.output
}
```


# Metabolite flux analysis

Load the required libraries
```{r message=FALSE,warning=FALSE}
library(OrganChat)
library(readr)
library(forcats)
library(METAFlux)
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Metabolite flux analysis

```{r, include=FALSE}
for (i in 1:length(UCI_Data_list)) {
  # Prepare the input RNA data 
  organ.select = names(UCI_Data_list)[i]
  Data.input_condition1 <- subset(UCI_Data_list[[organ.select]], subset = condition == condition.list[1])
  Data.input_condition2 <- subset(UCI_Data_list[[organ.select]], subset = condition == condition.list[2])
  Data.input_condition3 <- subset(UCI_Data_list[[organ.select]], subset = condition == condition.list[3])
  
  Data.input_condition1$Type <- fct_drop(Data.input_condition1$Type)
  Data.input_condition2$Type <- fct_drop(Data.input_condition2$Type)
  Data.input_condition3$Type <- fct_drop(Data.input_condition3$Type)
  # Update the Active Identity
  Data.input_condition1 <- SetIdent(Data.input_condition1, value = Data.input_condition1$Type)
  Data.input_condition2 <- SetIdent(Data.input_condition2, value = Data.input_condition2$Type)
  Data.input_condition3 <- SetIdent(Data.input_condition3, value = Data.input_condition3$Type)
  
  # METAFlux analysis
  Data.list = list(Condition1 = Data.input_condition1, Condition2 = Data.input_condition2, Condition3 = Data.input_condition3)
  names(Data.list) = condition.list
  
  for (j in 1:length(Data.list)) {
    flux = run_METAFlux(Data.input = Data.list[[j]],
                        myident = 'Type',
                        n_bootstrap=100, 
                        seed=1,
                        medium = human_blood)
    
    flux = METAFlux_reformat(flux = flux,
                             cell.types = levels(Data.list[[j]]@meta.data$Type),
                             exclude = "None",
                             METAFlux_lookup = METAFlux_lookup,
                             scale.byflux = TRUE)
    
    output = METAFlux_convert_OrganChat(cell.types = levels(Data.list[[j]]$Type),
                                       flux = flux,
                                       METAFlux_lookup = METAFlux_lookup,
                                       hmdb_dictionary = hmdb_dictionary)
    
    # write.csv(output , file = paste0(data.path, organ.select, "_flux_", names(Data.list[j]), ".csv"), 
    #           row.names = TRUE, col.names = TRUE)
  }
}
```
