---
title: "Sandra_CellRepMed_2023_DataProcessing_MetaboliteAnalysis"
output: html_document
date: "2026-04-28"
---

Processing the originl data and inferring metabolite flux level through OrganChat (based on METAFlux).
The original data comes from the following paper: Lilja S, Li X, Smelik M ... Multi-organ single-cell analysis reveals an on/off switch system with potential for personalized treatment of immunological diseases. Cell Reports Medicine, 2023; 4


```{r message=FALSE,warning=FALSE}
library(Seurat)
library(ggplot2)
library(patchwork)
library(RColorBrewer)
library(dplyr)
library(pheatmap)
library(ggraph)
library(forcats)
library(stringr)
library(plyr)
library(tidyverse)

library(METAFlux)
```


# Load and process the original data

Load the table of pro- and anti-inflammatory upstream regulators (URs), and the transcriptomics data provided by the paper.
```{r, include=FALSE}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/")

Inter_allorgans <- read_csv("Sandra_2023_Inter_allorgans.csv")
Sandra_2023_RNA <- readRDS("Sandra_2023_seu.rds")
```


For each organ in each condition, select clusters with more than 20 cells
```{r}
organ.list <- levels(Sandra_2023_RNA@meta.data$organ)
meta.data <- Sandra_2023_RNA@meta.data
rownames(meta.data) <- colnames(Sandra_2023_RNA@assays$RNA$data)

cell.use <- c()
for (i in 1:length(organ.list)) {
  cell.condition1 <- meta.data[meta.data$organ == organ.list[i] & meta.data$condition == "Sick", ]
  cell.condition2 <- meta.data[meta.data$organ == organ.list[i] & meta.data$condition == "Healthy", ]
  x1 <- aggregate(cell.condition1, by = list(cell.condition1$Type), length)
  x2 <- aggregate(cell.condition2, by = list(cell.condition2$Type), length)
  
  x1.cluster <- x1$Group.1[x1$Type > 20]
  x2.cluster <- x2$Group.1[x2$Type > 20]
  
  cluster.select <- intersect(x1.cluster, x2.cluster)
  cell.select <- rownames(meta.data)[meta.data$organ == organ.list[i] & meta.data$Type %in% cluster.select]
  cell.use <- c(cell.use, cell.select)
}

Sandra_2023_RNA <- subset(Sandra_2023_RNA, cells = cell.use)
```


Save the filtered data
```{r}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse")
# saveRDS(Sandra_2023_RNA, "Sandra_2023_mouse_filtered.rds")
```


# Convert the URs from human mouse genes

```{r, include=FALSE}
library(biomaRt)
library(edgeR)
library(clusterProfiler)
library(org.Hs.eg.db)
library(org.Mm.eg.db)
```


Function: convertGene -- find the homo genes based on the entrez id (human --> mouse)
```{r}
convertGene <- function(x){
  
  require(biomaRt)
  sp.to = useMart("ensembl", dataset = "mmusculus_gene_ensembl", host = "https://feb2014.archive.ensembl.org")
  sp.from = useMart("ensembl", dataset = "hsapiens_gene_ensembl", host = "https://feb2014.archive.ensembl.org")
  
  genes = getLDS(attributes = "ensembl_gene_id", values = x, mart = sp.from,
                 attributesL = c("mgi_symbol", "ensembl_gene_id"), martL = sp.to, uniqueRows = T)
  names(genes) <- c("ensembl_gene_id", "mgi_symbol", "ensembl_gene_id_converted")
  
  return(genes)
  
}
```


Export the URs and find their mouse homo genes
```{r}
Inter_all_target <- unique(Inter_allorgans$target)
Inter_all_target <- str_split(Inter_all_target, fixed("/"))

all.target = c()
for (i in 1:length(Inter_all_target)) {
  all.target <- unique(c(all.target, Inter_all_target[[i]]))
}

# get the ensembl id of the mouse genes
gene.from = data.frame(from = all.target)

gene_id <- getBM(attributes = c("ensembl_gene_id", "external_gene_name"), mart = useDataset("hsapiens_gene_ensembl", useMart("ensembl")))

gene.from <- merge(gene.from, gene_id[ , c(1,2)], by.x = "from", by.y = "external_gene_name" )
gene.from <- gene.from[complete.cases(gene.from), ]

gene_converted <- convertGene(gene.from$ensembl_gene_id)
gene_converted <- merge(gene.from, gene_converted[, c(1,2)], by = "ensembl_gene_id")

all.target.mouse <- intersect(gene_converted$mgi_symbol, rownames(Sandra_2023_RNA@assays$RNA@data))
```


Select the URs which are highly expressed (>1) in at least one cluster
```{r, include=FALSE}
library(exFINDER)

data.Sick <- subset(Sandra_2023_RNA, subset = condition == "Sick")
df.exp <- get_AveExp(Gene = all.target.mouse,
                     Exp.Data = data.Sick@assays$RNA@data,
                     Meta.Data = data.Sick@meta.data)

df.exp$max = apply(df.exp[, 2:ncol(df.exp)], 1, max)
all.target.mouse.Sick = df.exp$Gene[df.exp$max >1]

data.Healthy <- subset(Sandra_2023_RNA, subset = condition == "Healthy")
df.exp <- get_AveExp(Gene = all.target.mouse,
                     Exp.Data = data.Healthy@assays$RNA@data,
                     Meta.Data = data.Healthy@meta.data)

df.exp$max = apply(df.exp[, 2:ncol(df.exp)], 1, max)
all.target.mouse.Healthy = df.exp$Gene[df.exp$max >1]

# the final selections
all.target.mouse <- unique(c(all.target.mouse.Sick, all.target.mouse.Healthy))
all.target.mouse <- data.frame(targets = all.target.mouse)
```


Save the target genes
```{r}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/")

# write_excel_csv(all.target.mouse, file = "targets_highexpression.csv") 
```


# Infer metabolite flux data using human-converted Seurat object ("Sandra_2023_converted.rds")

Load the Seurat object (converted to human genes)
```{r}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/")

Sandra_2023_RNA <- readRDS("Sandra_2023_converted.rds")
```


Load metabolite dictionary data
```{r, include=FALSE}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/")

OrganChatDB_hmdb_dictionary <- read_csv("hmdb_dictionary_20240129.csv")
METAFlux_lookup <- read_csv("METAFlux_lookup_20240131.csv")
```


For each organ in each condition, select clusters with more than 20 cells
```{r}
organ.list <- levels(Sandra_2023_RNA@meta.data$organ)
meta.data <- Sandra_2023_RNA@meta.data
rownames(meta.data) <- colnames(Sandra_2023_RNA@assays$RNA$data)

cell.use <- c()
for (i in 1:length(organ.list)) {
  cell.condition1 <- meta.data[meta.data$organ == organ.list[i] & meta.data$condition == "Sick", ]
  cell.condition2 <- meta.data[meta.data$organ == organ.list[i] & meta.data$condition == "Healthy", ]
  x1 <- aggregate(cell.condition1, by = list(cell.condition1$Type), length)
  x2 <- aggregate(cell.condition2, by = list(cell.condition2$Type), length)
  
  x1.cluster <- x1$Group.1[x1$Type > 20]
  x2.cluster <- x2$Group.1[x2$Type > 20]
  
  cluster.select <- intersect(x1.cluster, x2.cluster)
  cell.select <- rownames(meta.data)[meta.data$organ == organ.list[i] & meta.data$Type %in% cluster.select]
  cell.use <- c(cell.use, cell.select)
}

Sandra_2023_RNA <- subset(Sandra_2023_RNA, cells = cell.use)
```


# Metabolite analysis (based on METAFlux)

```{r, include=FALSE}
setwd("~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/")
conditions = c("Sick", "Healthy")

for (i in 1:5) {
  # Prepare the input RNA data 
  organ.select = levels(Sandra_2023_RNA@meta.data$organ)[i]
  Data.input_condition1 <- subset(Sandra_2023_RNA, subset = organ == organ.select &
                                    # Type %in% cluster.top &
                                    condition == conditions[1])
  
  Data.input_condition2 <- subset(Sandra_2023_RNA, subset = organ == organ.select &
                                    # Type %in% cluster.top &
                                    condition == conditions[2])
  
  Data.input_condition1$Type <- fct_drop(Data.input_condition1$Type)
  Data.input_condition2$Type <- fct_drop(Data.input_condition2$Type)
  # Update the Active Identity
  Data.input_condition1 <- SetIdent(Data.input_condition1, value = Data.input_condition1$Type)
  Data.input_condition2 <- SetIdent(Data.input_condition2, value = Data.input_condition2$Type)
  
  # METAFlux analysis
  Data.list = list(Condition1 = Data.input_condition1, Condition2 = Data.input_condition2)
  names(Data.list) = conditions
  
  for (j in 1:length(Data.list)) {
    flux = run_METAFlux(Data.input = Data.list[[j]],
                        myident = 'Type',
                        n_bootstrap=100, 
                        seed=1,
                        medium = human_blood)
    
    flux = METAFlux_reformat(flux = flux,
                             cell.types = levels(Data.list[[j]]@meta.data$Type),
                             exclude = "None",
                             METAFlux_lookup = METAFlux_lookup,
                             scale.byflux = TRUE)
    
    output = METAFlux_convert_OrganChat(cell.types = levels(Data.list[[j]]$Type),
                                       flux = flux,
                                       METAFlux_lookup = METAFlux_lookup,
                                       hmdb_dictionary = hmdb_dictionary)
    
   #  write.csv(output , file = paste0(organ.select, "_flux_", names(Data.list[j]), ".csv"), 
   #            row.names = TRUE, col.names = TRUE)
  }
}
```
