---
title: "Sandra_CellRepMed_2023_MOOC"
author: "Changhan"
date: "2024-08-10"
output: html_document
---

Perform multi-organ OrganChat (MOOC) Analysis of OrganChat between conditions for: joint, muscle, lung, skin, spleen.

```{r message=FALSE,warning=FALSE}
library(OrganChat)
library(readr)
library(forcats)
```


# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/"    # your path to the ouput folder
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```

# Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```


Load the scRNA-seq data and the targets
```{r, include=FALSE}
Sandra_2023_RNA <- readRDS(paste0(data.path, "Sandra_2023_mouse_filtered.rds") )
targets <- read_csv(paste0(data.path, "targets_highexpression.csv") )
```


Create data inputs
```{r}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("joint", "muscle", "lung", "skin", "spleen")
conditions = c("Sick", "Healthy")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- subset(Sandra_2023_RNA, subset = organ == organ.select)
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}
```

Create OC object
```{r}
MOOC = create_OrganChat(object = data.list, 
                        organs = organs,
                        idents.list = idents.list, 
                        ComparisonAnalysis = TRUE,
                        conditions = conditions,
                        conditions.list = conditions.list,
                        assay = NULL, 
                        do.sparse = T)
```

Integrate the scRNA-seq data
```{r}
MOOC = MO_cal_scRNA.bygroup(object = MOOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```



Prepare the metabolite flux data
```{r, include=FALSE}
organs = MOOC@organs

metalist.1 = list()
metalist.2 = list()

for (i in 1:5) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

Integrate the flux data
```{r}
MOOC <- MO_merge_metabolite.bygroup(object = MOOC,
                                    metabolitedata.list.condition1 = metalist.1,
                                    metabolitedata.list.condition2 = metalist.2,
                                    type = "flux",
                                    scale.max = 10)
```

Pairwise analysis (~45min)
```{r}
start.time <- Sys.time()

MOOC.net <- MO_pairwise_analysis(object = MOOC,
                             DB = OrganChatDB, 
                             LS = NULL, 
                             receptor = NULL, 
                             tf = NULL,
                             target = targets$targets,
                             K = 0.1, 
                             N = 1,
                             R = 100,
                             CI = 0.95,
                             CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                             CA_cutoff_chatP = 0.2,
                             CA_cutoff_sd = NULL,
                             CA_cutoff_CI = 0)

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```


```{r}
# saveRDS(MOOC.net, paste0(data.path, "MOOCnet.rds"))
```



Visualization
category -- "All", "hormone_peptide", "cytokines", "hormone_nonpeptide", "metabolite"

style = "ave.weight"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "All",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "ave.weight")
```



style = "ave.weight"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "cytokines",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "ave.weight")
```

style = "ave.weight"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "metabolite",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "ave.weight")
```

style = "ave.weight"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "ave.weight")
```

style = "ave.weight"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_nonpeptide",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "ave.weight")
```

style = "total.counts"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "All",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts")
```

style = "total.counts"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "cytokines",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts")
```

style = "total.counts"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "metabolite",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts")
```

style = "total.counts"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts")
```

style = "total.counts"
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_nonpeptide",
                                chatP_cutoff = 0.5)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts")
```

################################################################################

Load the list of GRN for MOOC
```{r}
# setwd("/Volumes/Samsung_T5/OrganChat/Examples/Sandra_CellRepMed_2023/Data")
# MOOC.net <- readRDS("MOOCnet.rds")
```


Get the inferred targets list
```{r}
inferred.targets = c()

for ( i in 1:(length(MOOC.net)-1) ) {
  for ( j in 1:2 ) {
    for ( k in 1:4 ) {
      df = MOOC.net[[i]][[j]][[k]]
      for ( ii in 1:length(df) ) {
        if( nrow(df[[ii]])>0 ){
          inferred.targets = c(inferred.targets, df[[ii]]$Target)
        }
      }
    }
  }
}

inferred.targets = unique(inferred.targets)
```


Get their average expression data
```{r}
DGdata <- MOOC@DGdata

list.1 <- list()
list.2 <- list()
group.organ <- c()

for (i in 1:5) {
  list.1[[i]] = data.frame( t(DGdata[[1]][[i]][ inferred.targets, ]) )
  rownames(list.1[[i]]) = paste0(rownames(list.1[[i]]), "_", names(DGdata[[1]][i]))
  list.2[[i]] = data.frame( t(DGdata[[2]][[i]][ inferred.targets, ]) )
  rownames(list.2[[i]]) = paste0(rownames(list.2[[i]]), "_", names(DGdata[[2]][i]))
  
  group.organ <- c(group.organ, rownames(list.1[[i]]))
}

expdata.1 <- data.frame( t(rbindlist(list.1)) )
expdata.2 <- data.frame( t(rbindlist(list.2)) )

colnames(expdata.1) = group.organ
colnames(expdata.2) = group.organ
```


Calculate the log2 fold change
```{r}
expdata.1[expdata.1 < 0.05] = 0.05
expdata.2[expdata.2 < 0.05] = 0.05

log2fc.df <- log2(expdata.1/expdata.2)

df.plot = as.matrix(log2fc.df)
df.plot[df.plot >= 3] = 3
df.plot[df.plot < 3 & df.plot > 1] = 2
df.plot[df.plot <= 1 & df.plot > 0.1] = 1
df.plot[df.plot <= 0.1 & df.plot >= -0.1] = 0
df.plot[df.plot < -0.1 & df.plot >= -1] = -1
df.plot[df.plot < -1 & df.plot > -3] = -2
df.plot[df.plot <= -3] = -3
```

Plot the heatmap
```{r}
bk <- c(seq(-3, 3, by = 1))

col_cluster_list <- str_split(colnames(df.plot), fixed("_"))
col_cluster = c()
for (i in 1:length(col_cluster_list)) {
  col_cluster = c(col_cluster, col_cluster_list[[i]][[1]])
}

col_anno = data.frame(clusters = col_cluster,
                      organs = c(rep("joint",5), rep("muscle",7), rep("lung",2), rep("skin",3), rep("spleen",6)))
rownames(col_anno) = colnames(df.plot)
col_anno$organs = factor(col_anno$organs, levels = c("joint", "muscle", "lung", "skin", "spleen"))
col_anno$clusters = factor(col_anno$clusters)

mycolors.organ = brewer.pal(8, "Set2")[1:5]
set.seed(1)
mycolors.cluster = rand_color(length(levels(col_anno$clusters)), transparency = 0.2)
names(mycolors.organ) <- c("joint", "lung", "muscle", "skin", "spleen")
names(mycolors.cluster) <- levels(col_anno$clusters)
# mycolors = c(mycolors.organ, mycolors.cluster)
# names(mycolors) <- c(c("joint", "lung", "muscle", "skin", "spleen"), levels(col_anno$clusters))
mycolors <- list(organs = mycolors.organ, clusters = mycolors.cluster)

legend_anno = c("below -3", "-3 ~ -1", "-1 ~ -0.1", "-0.1 ~ 0.1", "0.1 ~ 1", "1 ~ 3", "above 3")


pdf(paste0(output.dir, "targets_Heatmap_log2fc.pdf"), width=8, height = 12)

pheatmap(df.plot,
         cluster_cols = F,
         cluster_rows = F,
         scale = "none",
         legend_breaks = bk, 
         legend_labels = legend_anno,
         annotation_col = col_anno,
         annotation_colors = mycolors,
         border_color = "grey80",
         color = colorRampPalette(c("royalblue3", "white", "tomato3"))(length(bk)),
         breaks = bk, 
         cellheight = 10, 
         cellwidth = 10,
         labels_col = c(rep("", 23)))

dev.off()

set.seed(NULL)
```


