---
title: "Sandra_CellRepMed_2023_CAOC"
author: "Changhan"
date: "2024-08-11"
output: html_document
---

Perform Comparison analysis of OrganChat between conditions for: joint and muscle; joint and spleen; muscle and spleen; skin and muscle.

```{r message=FALSE,warning=FALSE}
library(OrganChat)
library(readr)
library(forcats)
```


# Preparation

```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Sandra_2023_mouse/"    # your path to the ouput folder
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```

# Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```


Load the scRNA-seq data and the targets
```{r, include=FALSE}
Sandra_2023_RNA <- readRDS(paste0(data.path, "Sandra_2023_mouse_filtered.rds") )
targets <- read_csv(paste0(data.path, "targets_highexpression.csv") )
```


################################################################################
# Comparative analysis (joint, muscle)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("joint", "muscle")
conditions = c("Sick", "Healthy")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- subset(Sandra_2023_RNA, subset = organ == organ.select)
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
target = targets$targets

CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = NULL, 
                     receptor = NULL, 
                     tf = NULL,
                     target = target)
```


Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC)
```

OrganChat object for joint & muscle
```{r}
CAOC_jm = CAOC
```



## Visualization

Chord diagram: joint -> muscle, total counts of LS-T pathways with communication probability > 0.3, sick vs. healthy
```{r}
CAOC_chorddiagram(object = CAOC_jm,
                  dir = "forward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


Chord diagram: joint <- muscle, total counts of LS-T pathways with communication probability > 0.3, sick vs. healthy
```{r}
CAOC_chorddiagram(object = CAOC_jm,
                  dir = "backward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


river plot:  joint (Fibroblasts) -> muscle (Neutrophils), sick condition
```{r}
df.plot = CAOC_jm@net$Sick$forward$Fibroblasts_to_Neutrophils

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


rose diagram: joint (Fibroblasts) -> muscle (Neutrophils), sick condition
```{r}
components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)
```


bubble heatmap:  joint -> muscle, all inferred LS-T Pathways, sick vs. healthy 
```{r}
CAOC_bubbleheatmap(object = CAOC_jm,
                  dir = "forward",
                  category = "All",
                  size = "total.counts",
                  color = "ave.weight",
                  ncol = 2)
```


Bar plot of the LS-T pathways with the highest differential index (DI), from joint (Neutrophils) to muscle, driven by Adenine.
```{r}
df.plot = CAOC_jm@DEpath[CAOC_jm@DEpath$Direction == "forward" & 
                           CAOC_jm@DEpath$Receiver.group == "Neutrophils" & 
                           CAOC_jm@DEpath$LS_name %in% c("Adenine"), ]

CAOC_DI_barplot(df = df.plot,
                n = 5,
                axis.text.size = 50)
```


GO enrichment analysis of the targets in joint (Neutrophils) to muscle (NK) communication under sick condition
```{r}
x = OC_GOanalysis(df =CAOC_jm@net$Sick$forward$`Endothelial cells_to_NK cells`,
                  LS = NULL,
                  layer = "Target")

# plot top 10 GO terms
GOanalysis_scatterplot(df = x$result,
                       n = 10,
                       size=6)
```


GO enrichment analysis of the targets in joint (Fibroblasts) to muscle (Endothelial) communication under sick condition
```{r}
x = OC_GOanalysis(df =CAOC_jm@net$Sick$forward$`Fibroblasts_to_Endothelial cells`,
                  LS = NULL,
                  layer = "Target")

# plot top 10 GO terms
GOanalysis_scatterplot(df = x$result,
                       n = 10,
                       size=6)
```


################################################################################
# Comparative analysis (joint, spleen)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("joint", "spleen")
conditions = c("Sick", "Healthy")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- subset(Sandra_2023_RNA, subset = organ == organ.select)
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
target = targets$targets

CAOC = CA_net0_infer(object = CAOC,
                         DB = OrganChatDB, 
                         LS = NULL, 
                         receptor = NULL, 
                         tf = NULL,
                         target = target)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                        Sender.group = NULL,
                        Receiver.group = NULL,
                        Direction = NULL,
                        p_cutoff = NULL,
                        sd_cutoff = NULL,
                        DI_cutoff = NULL,
                        top = NULL)
```


```{r}
CAOC_js = CAOC
```



## Visualization

Chorddiagram
```{r}
CAOC_chorddiagram(object = CAOC_js,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_js,
                  dir = "backward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_js,
                  dir = "backward",
                  category = "All",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_js,
                  dir = "backward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_js,
                  dir = "backward",
                  category = "metabolite",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)

```


riverplot
```{r}
df.plot = CAOC_js@net$Sick$backward$`Dendritic cells_to_Fibroblasts`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


bubbleheatmap
```{r}
CAOC_bubbleheatmap(object = CAOC_js,
                  dir = "backward",
                  category = "All",
                  size = "total.counts",
                  color = "ave.weight")
```


RI_barplot
```{r}
df.plot = CAOC_js@DEpath[CAOC_js@DEpath$Direction == "backward", ]

CAOC_DI_barplot(df = df.plot,
                n = 5,
                axis.text.size = 50)
```



```{r}
df.plot = CAOC_js@DEpath[CAOC_js@DEpath$Direction == "backward" & 
                        CAOC_js@DEpath$category == "metabolite" & 
                        # CAOC_js@DEpath$Sender.group %in% c("B cells", "T cells") &
                        CAOC_js@DEpath$Receiver.group == "Fibroblasts", ]

CAOC_DI_barplot(df = df.plot,
                n = 5,
                axis.text.size = 50)
```


```{r}
x = OC_GOanalysis(df =CAOC_js@net$Sick$backward$`Dendritic cells_to_Fibroblasts`,
                  LS = NULL,
                  layer = "Target")

GOanalysis_scatterplot(df = x$result,
                       n = 10,
                       size=6)
```



################################################################################
# Comparative analysis (muscle, spleen)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("muscle", "spleen")
conditions = c("Sick", "Healthy")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- subset(Sandra_2023_RNA, subset = organ == organ.select)
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
target = targets$targets

CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = NULL, 
                     receptor = NULL, 
                     tf = NULL,
                     target = target)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                        Sender.group = NULL,
                        Receiver.group = NULL,
                        Direction = NULL,
                        p_cutoff = NULL,
                        sd_cutoff = NULL,
                        DI_cutoff = NULL,
                        top = NULL)
```


```{r}
CAOC_ms = CAOC
```



## Visualization

```{r}
CAOC_chorddiagram(object = CAOC_ms,
                  dir = "backward",
                  category = "All",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```



```{r}
CAOC_chorddiagram(object = CAOC_ms,
                  dir = "backward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_ms,
                  dir = "backward",
                  category = "metabolite",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```


```{r}

CAOC_chorddiagram(object = CAOC_ms,
                  dir = "backward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```

DI_barplot
```{r}
df.plot = CAOC_ms@DEpath[CAOC_ms@DEpath$Direction == "backward" & 
                        CAOC_ms@DEpath$Sender.group %in% c("T cells") , ]

CAOC_DI_barplot(df = df.plot,
                n = 5,
                axis.text.size = 50)
```


################################################################################
# Comparative analysis (skin, muscle)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("skin", "muscle")
conditions = c("Sick", "Healthy")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- subset(Sandra_2023_RNA, subset = organ == organ.select)
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
target = targets$targets

CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = NULL, 
                     receptor = NULL, 
                     tf = NULL,
                     target = target)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                        Sender.group = NULL,
                        Receiver.group = NULL,
                        Direction = NULL,
                        p_cutoff = NULL,
                        sd_cutoff = NULL,
                        DI_cutoff = NULL,
                        top = NULL)
```


```{r}
CAOC_skm = CAOC
```


## Visualization
Chorddiagram
```{r}
CAOC_chorddiagram(object = CAOC_skm,
                  dir = "forward",
                  category = "All",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_skm,
                  dir = "forward",
                  category = "metabolite",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_skm,
                  dir = "forward",
                  category = "cytokines",
                  style = "ave.weight",
                  chatP_cutoff = 0.3)
```




```{r}
CAOC_chorddiagram(object = CAOC_skm,
                  dir = "forward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


```{r}
CAOC_chorddiagram(object = CAOC_skm,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.3)
```


################################################################################

# Additional visualizations

```{r}
df.plot = CAOC_jm@net$Sick$forward$Fibroblasts_to_Neutrophils

x = OC_GOanalysis(df = df.plot,
                  LS = NULL,
                  layer = "Target")

GOanalysis_scatterplot(df = x$result,
                       n = 10,
                       size=6)
```


```{r}
x = construct_Network_df(df = df.plot,
                         category = "All",
                         restrict.by = "Both")
# S100a8-driven GRN
network_treeplot(x[20])

# Lgals1-to-Cd14 GRN
network_treeplot(x[39])
```


```{r}
df.plot = CAOC_jm@DEpath[CAOC_jm@DEpath$Direction == "forward" & 
                        CAOC_jm@DEpath$Receiver.group %in% c("Neutrophils") &
                          CAOC_jm@DEpath$LS_name %in% c("Adenine"), ]

CAOC_DI_barplot(df = df.plot,
                n = 3,
                axis.text.size = 50)
```

```{r}
df.plot = CAOC_jm@DEpath[CAOC_jm@DEpath$Direction == "forward" & 
                           CAOC_jm@DEpath$Sender.group %in% c("Fibroblasts") &
                           CAOC_jm@DEpath$Receiver.group %in% c("Neutrophils") &
                           CAOC_jm@DEpath$LS_name %in% c("Adenine"), ]

CAOC_DI_barplot(df = df.plot,
                n = 3,
                axis.text.size = 50)
```



```{r}
df.plot = CAOC_ms@net$Sick$backward$Monocytes_to_Neutrophils

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


```{r}
df.plot = CAOC_ms@net$Healthy$backward$`B cells_to_Endothelial cells`

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


```{r}
df.plot = CAOC_ms@DEpath[CAOC_ms@DEpath$Direction == "backward" & 
                        CAOC_ms@DEpath$Receiver.group %in% c("Endothelial cells") &
                          CAOC_ms@DEpath$Sender.group %in% c("B cells"), ]

CAOC_DI_barplot(df = df.plot,
                n = 10,
                axis.text.size = 50)
```

```{r}
df.plot = CAOC_skm@net$Sick$forward$Fibroblasts_to_Macrophages

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


```{r}
df.plot = CAOC_skm@net$Healthy$forward$Fibroblasts_to_Macrophages

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```



```{r}
df.plot = CAOC_skm@DEpath[CAOC_skm@DEpath$Direction == "forward" & 
                        CAOC_skm@DEpath$Receiver.group %in% c("Macrophages") &
                          CAOC_skm@DEpath$Sender.group %in% c("Fibroblasts"), ]

CAOC_DI_barplot(df = df.plot,
                n = 10,
                axis.text.size = 50)
```


