---
title: "HumanAtlas_Science_2022_Multi-OrganAnalysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HumanAtlas_Science_2022_Multi-OrganAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


Inferring organ-organ communication between Spleen, Small_Intestine, Lymph_Node, Lung, and Vasculature.


```{r setup}
library(OrganChat)
library(readr)
library(forcats)
```

# Preparation

Please set your paths to the necessary files below
```{r}
data.path = "~/Documents/OrganChat_v3/HumanAtlas_Science_2022/Data/"
DB.path = "~/Documents/OrganChat_v3/Database/"
Dictionary.path = "~/Documents/OrganChat_v3/Metabolite_Dictionary/"
output.dir = "~/Documents/OrganChat_v3/HumanAtlas_Science_2022/Outputs/"
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
load(paste0(DB.path, "LSR_layer1_human.rda")) # set your path load the LS-R database for human
load(paste0(DB.path, "RSE_layer2_human.rda")) # set your path load the R-SE database for human
load(paste0(DB.path, "SET_layer3_human.rda")) # set your path load the SE-T database for human

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_human
OrganChatDB[[2]] <- RSE_layer2_human
OrganChatDB[[3]] <- SET_layer3_human
```



Load the Seurat object
c("Spleen", "Small_Intestine", "Lymph_Node", "Bladder", "Lung", "Vasculature")
```{r}
CAOC.organ.list <- c("Spleen", "Small_Intestine", "Lymph_Node", "Lung", "Vasculature")

TS_Data_list <- list()

for (i in 1:length(CAOC.organ.list)) {
  TS_Data_list[[i]] = readRDS(paste0(data.path, "TS_", CAOC.organ.list[i], "_downsampled.rds")) # set your path load the downsampled data for each organ
}

names(TS_Data_list) = CAOC.organ.list
```


Marker gene analysis
```{r}
markergenes.list = list()

for (i in 1:length(TS_Data_list)) {
  
  Data.input = TS_Data_list[[i]]
  
  # Update the Active Identity
  Data.input@meta.data$marker_ID = paste0(Data.input@meta.data$Type, "_", Data.input@meta.data$condition)
  Data.input <- SetIdent(Data.input, value = Data.input$marker_ID)
  
  Data.input.markers <- FindAllMarkers(Data.input, only.pos = TRUE)
  
  colnames(Data.input.markers)[6] = "marker_ID"
  Data.input.markers$cluster = str_split_fixed(Data.input.markers$marker_ID, fixed("_"), n=3)[ , 1]
  Data.input.markers$condition = str_split_fixed(Data.input.markers$marker_ID, fixed("_"), n=3)[ , 2]
  Data.input.markers$organ = names(TS_Data_list[i])
  
  markergenes.list[[i]] = Data.input.markers
}

markergenes = rbindlist(markergenes.list)

# write_csv(markergenes, paste0(data.path, "humanatlas_markergenes_5organs.csv"))
```


select top 5 markers if each cluster as the targets (from both organs)
```{r}
markergenes = read_csv(paste0(data.path, "humanatlas_markergenes_5organs.csv") ) # set your path load the list of marker genes

N = 5

targets = c()

for (i in 1:length(TS_Data_list)) {
  
  markergenes.organ = markergenes[markergenes$organ == names(TS_Data_list[i]), ]
  markergenes.organ %>%
    group_by(marker_ID) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = N) %>%
    ungroup() -> top.markers
  
  targets = c(targets, top.markers$gene)
}

targets = unique(targets)
```

# Multi-organ organchat (MOOC) analysis 

Create data inputs
```{r}
data.list = list()
idents.list = list()

organs = names(TS_Data_list)
conditions = c("female", "male")

for (i in 1:length(TS_Data_list)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- TS_Data_list[[i]]
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}
```


Create OC object
```{r}
MOOC = create_OrganChat(object = data.list, 
                        organs = organs,
                        idents.list = idents.list, 
                        ComparisonAnalysis = TRUE,
                        conditions = conditions,
                        conditions.list = conditions.list,
                        assay = NULL, 
                        do.sparse = T)
```

Integrate the scRNA-seq data
```{r}
MOOC = MO_cal_scRNA.bygroup(object = MOOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```



Prepare the metabolite flux data
```{r, include=FALSE}
organs = MOOC@organs

metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") ) # set your path load the metabolite flux data for each organ, condition 1
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv")) # set your path load the metabolite flux data for each organ, condition 2
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```

Integrate the flux data
```{r}
MOOC <- MO_merge_metabolite.bygroup(object = MOOC,
                                    metabolitedata.list.condition1 = metalist.1,
                                    metabolitedata.list.condition2 = metalist.2,
                                    type = "flux",
                                    scale.max = 10)
```

Pairwise analysis (~2.09hours)
```{r}
start.time <- Sys.time()

MOOC.net <- MO_pairwise_analysis(object = MOOC,
                             DB = OrganChatDB, 
                             LS = NULL, 
                             receptor = NULL, 
                             tf = NULL,
                             target = targets,
                             K = 0.1, 
                             N = 1,
                             R = 100,
                             CI = 0.95,
                             CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                             CA_cutoff_chatP = 0.2,
                             CA_cutoff_sd = NULL,
                             CA_cutoff_CI = 0)

end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken
```


# Visualization
category -- "All", "hormone_peptide", "cytokines", "hormone_nonpeptide", "metabolite"

Circle plot: number of LS-T pathways with communication probability > 0.75 between organs.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "All",
                                chatP_cutoff = 0.75)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts",
               scale.edge.width = 8,
               scale.vertex.size = 40)
```

Circle plot: number of peptide hormone-driven LS-T pathways with communication probability > 0.75 between organs.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_peptide",
                                chatP_cutoff = 0.75)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts",
               scale.edge.width = 8,
               scale.vertex.size = 40)

```


Circle plot: number of non-peptide hormone-driven LS-T pathways with communication probability > 0.75 between organs.
```{r}
# Construct the network
MOOC.plot <- MO_networkconstruct(object = MOOC,
                                MO.net.list = MOOC.net,
                                category = "hormone_nonpeptide",
                                chatP_cutoff = 0.75)

MO_networkplot(network.input = MOOC.plot,
               style = "total.counts",
               scale.edge.width = 8,
               scale.vertex.size = 40)
```
