---
title: "HumanAtlas_Science_2022_ComparisonAnalysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HumanAtlas_Science_2022_ComparisonAnalysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Perform comparison analysis via organchat (CAOC) between Small_Intestine and Vasculature, Lung and Vasculature, Lymph node and Vasculature, respectively.

```{r setup}
library(OrganChat)
library(readr)
library(forcats)
```


# Preparation

Please set your paths to the necessary files below
```{r}
data.path = "~/Documents/OrganChat_v3/HumanAtlas_Science_2022/Data/"
DB.path = "~/Documents/OrganChat_v3/Database/"
Dictionary.path = "~/Documents/OrganChat_v3/Metabolite_Dictionary/"
output.dir = "~/Documents/OrganChat_v3/HumanAtlas_Science_2022/Outputs/"
```


Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
load(paste0(DB.path, "LSR_layer1_human.rda")) # set your path load the LS-R database for human
load(paste0(DB.path, "RSE_layer2_human.rda")) # set your path load the R-SE database for human
load(paste0(DB.path, "SET_layer3_human.rda")) # set your path load the SE-T database for human

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_human
OrganChatDB[[2]] <- RSE_layer2_human
OrganChatDB[[3]] <- SET_layer3_human
```


Load the Seurat object
c("Spleen", "Small_Intestine", "Lymph_Node", "Bladder", "Lung", "Vasculature")
```{r}
CAOC.organ.list <- c("Spleen", "Small_Intestine", "Lymph_Node", "Lung", "Vasculature")

TS_Data_list <- list()

for (i in 1:length(CAOC.organ.list)) {
  TS_Data_list[[i]] = readRDS(paste0(data.path, "TS_", CAOC.organ.list[i], "_downsampled.rds")) # set your path load the downsampled data for each organ
}

names(TS_Data_list) = CAOC.organ.list
```


# Comparative analysis (Small_Intestine, Vasculature)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("Small_Intestine", "Vasculature")
conditions = c("female", "male")

for (i in 1:length(organs)) {
  organ.select = organs[i]

  Data.input_organ <- TS_Data_list[[organ.select]]
  data.list[[i]] = Data.input_organ@assays$RNA@data
  # ident.list
  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  # condition.list
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

# load flux data
for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") ) # set your path load the metabolite flux data for each organ, condition 1
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv")) # set your path load the metabolite flux data for each organ, condition 2
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```


select top 15 markers if each cluster as the targets (from both organs)
```{r}
markergenes = read_csv(paste0(data.path, "humanatlas_markergenes_5organs.csv") ) # set your path load the list of marker genes

N = 15
targets = c()
for (i in 1:length(organs)) {
  
  markergenes.organ = markergenes[markergenes$organ == organs[i], ]
  markergenes.organ %>%
    group_by(marker_ID) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = N) %>%
    ungroup() -> top.markers
  
  targets = c(targets, top.markers$gene)
}

targets = unique(targets)
```


## OrganChat comparison analysis (CAOC)
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = NULL, 
                     receptor = NULL, 
                     tf = NULL,
                     target = targets)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                    Sender.group = NULL,
                    Receiver.group = NULL,
                    Direction = NULL,
                    p_cutoff = NULL,
                    sd_cutoff = NULL,
                    DI_cutoff = NULL,
                    top = NULL)
```

Save the object
```{r}
CAOC_SiVa = CAOC

# saveRDS(CAOC_SiVa, file = paste0(data.path, "CAOC_SiVa.rds"))
```



## Visualization

Chord diagram: Small intestine -> Vasculature, total counts of LS-T pathways with communication probability > 0.75, female vs. male.
```{r}
CAOC_chorddiagram(object = CAOC_SiVa,
                  dir = "forward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.75)
```

Chord diagram: Small intestine <- Vasculature, total counts of LS-T pathways with communication probability > 0.75, female vs. male.
```{r}
CAOC_chorddiagram(object = CAOC_SiVa,
                  dir = "backward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.75)
```

Chord diagram: Small intestine -> Vasculature, total counts of LS-T pathways with communication probability > 0.75 and LS is metabolite, female vs. male.
```{r}
CAOC_chorddiagram(object = CAOC_SiVa,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.75)
```



river plot:  Small intestine (epithelial) -> Vasculature (stromal), female
```{r}
df.plot = CAOC_SiVa@net$female$forward$epithelial_to_stromal

OC_riverplot_test(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20)
```


river plot:  Small intestine (stromal) -> Vasculature (stromal), female
```{r}
df.plot = CAOC_SiVa@net$female$forward$stromal_to_endothelial

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


river plot:  Small intestine (immune) -> Vasculature (stromal), male
```{r}
df.plot = CAOC_SiVa@net$male$forward$immune_to_stromal

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


rose diagram: Small intestine (stromal) <- Vasculature (immune), metabolite-driven, male
```{r}
df.plot = CAOC_SiVa@net$male$backward$immune_to_stromal

components_rosediagram(df = df.plot, 
                       category = "metabolite",
                       n = 5)
```


rose diagram: Small intestine (endothelial) <- Vasculature (immune), female
```{r}
df.plot = CAOC_SiVa@net$female$backward$immune_to_endothelial

components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)
```


rose diagram & river plot: Small intestine (immune) -> Vasculature (stromal), male
```{r}
df.plot = CAOC_SiVa@net$male$forward$immune_to_stromal

components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


rose diagram & river plot: Small intestine (immune) -> Vasculature (stromal), metabolite-driven, female
```{r}
df.plot = CAOC_SiVa@net$female$forward$immune_to_stromal

components_rosediagram(df = df.plot, 
                       category = "metabolite",
                       n = 5)

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


# Comparative analysis (Lung, Vasculature)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("Lung", "Vasculature")
conditions = c("female", "male")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- TS_Data_list[[organ.select]]
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```


select top 15 markers if each cluster as the targets (from both organs)
```{r}
markergenes = read_csv(paste0(data.path, "humanatlas_markergenes_5organs.csv") )

N = 15

targets = c()

for (i in 1:length(organs)) {
  
  markergenes.organ = markergenes[markergenes$organ == organs[i], ]
  markergenes.organ %>%
    group_by(marker_ID) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = N) %>%
    ungroup() -> top.markers
  
  targets = c(targets, top.markers$gene)
}

targets = unique(targets)
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
CAOC = CA_net0_infer(object = CAOC,
                         DB = OrganChatDB, 
                         LS = NULL, 
                         receptor = NULL, 
                         tf = NULL,
                         target = targets)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                        Sender.group = NULL,
                        Receiver.group = NULL,
                        Direction = NULL,
                        p_cutoff = NULL,
                        sd_cutoff = NULL,
                        DI_cutoff = NULL,
                        top = NULL)
```

save the object
```{r}
CAOC_LuVa = CAOC

# saveRDS(CAOC_LuVa, file = paste0(data.path, "CAOC_LuVa.rds"))
```


## Visualization

Chord diagram: Lung -> Vasculature, total counts of metabolite-driven LS-T pathways with communication probability > 0.75, female vs. male.
```{r}
CAOC_chorddiagram(object = CAOC_LuVa,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.75)
```


Chord diagram: Lung <- Vasculature, total counts of LS-T pathways with communication probability > 0.75, female vs. male.
```{r}
CAOC_chorddiagram(object = CAOC_LuVa,
                  dir = "backward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.75)
```


rose diagram & river plot: Lung (epithelial) <- Vasculature (stromal), male
```{r}
df.plot = CAOC_LuVa@net$male$backward$stromal_to_epithelial

components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```


rose diagram & river plot: Lung (epithelial) <- Vasculature (stromal), female
```{r}
df.plot = CAOC_LuVa@net$female$backward$stromal_to_epithelial

components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)
```



Bubble plot of Small intestine -> Vasculature, total counts of pathways between conditions (female vs male) with communication probability > 0.6.
```{r}
LS.name = c()
female.size = c()
male.size = c()

for (i in c(17, 12, 4, 31, 15, 14)) {
  
  df.plot = CAOC_SiVa@DEpath[CAOC_SiVa@DEpath$Direction == "forward" & 
                        CAOC_SiVa@DEpath$LS_name == unique(CAOC_SiVa@DEpath[CAOC_SiVa@DEpath$Direction == "forward", ]$LS_name)[i] , ]
  
  LS.name = c(LS.name, unique(df.plot$LS_name))
  
  female.size = c(female.size, nrow(df.plot[df.plot$chatP_female > 0.6, ]))
  male.size = c(male.size, nrow(df.plot[df.plot$chatP_male > 0.6, ]))
}

df1 = data.frame(LS.name = LS.name, size = female.size, sex = "female")
df2 = data.frame(LS.name = LS.name, size = male.size, sex = "male")
df = rbind(df1, df2)

# pdf(paste0(output.dir, "CAOC_bubble_SiVa_forward_LS_pathwaynumbers.pdf"), width = 12, height = 8)

ggplot(df, aes(sex, LS.name, size = size, color = factor(LS.name))) +
  geom_point(alpha = 0.7) +
  scale_size(range = c(1, 12), name = "Number of pathway") +
  scale_color_brewer(palette = "Set1") +
  xlab("Receiver group") + ylab("Sender group") +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  theme(axis.text.x = element_text(hjust = 1))

# dev.off()
```


Bubble plot of Lung <- Vasculature, total counts of pathways between conditions (female vs male) with communication probability > 0.6.
```{r}
LS.name = c()
female.size = c()
male.size = c()

for (i in c(3, 16, 30, 17, 21, 32, 9)) {
  
  df.plot = CAOC_LuVa@DEpath[CAOC_LuVa@DEpath$Direction == "backward" & 
                        CAOC_LuVa@DEpath$LS_name == unique(CAOC_LuVa@DEpath[CAOC_LuVa@DEpath$Direction == "backward", ]$LS_name)[i] , ]
  
  LS.name = c(LS.name, unique(df.plot$LS_name))
  
  female.size = c(female.size, nrow(df.plot[df.plot$chatP_female > 0.6, ]))
  male.size = c(male.size, nrow(df.plot[df.plot$chatP_male > 0.6, ]))
}

df1 = data.frame(LS.name = LS.name, size = female.size, sex = "female")
df2 = data.frame(LS.name = LS.name, size = male.size, sex = "male")
df = rbind(df1, df2)

# pdf(paste0(output.dir, "CAOC_bubble_LuVa_backward_LS_pathwaynumbers.pdf"), width = 12, height = 8)

ggplot(df, aes(sex, LS.name, size = size, color = factor(LS.name))) +
  geom_point(alpha = 0.7) +
  scale_size(range = c(1, 12), name = "Number of pathway") +
  scale_color_brewer(palette = "Dark2") +
  xlab("Receiver group") + ylab("Sender group") +
  theme_bw() +
  theme(panel.grid = element_blank()) +
  theme(axis.text.x = element_text(hjust = 1))

# dev.off()
```


Tree plot of GRN connecting LTB4 and IGFBP5 in Small intestine -> Vasculature communication in male.
```{r}
df.plot = CAOC_SiVa@net$male$forward$immune_to_stromal
df.plot = df.plot[df.plot$LS_name == unique(CAOC_SiVa@DEpath[CAOC_SiVa@DEpath$Direction == "forward", ]$LS_name)[17] &
                    df.plot$Target %in% c("IGFBP5"), ]
df.plot %>%
  group_by(Target) %>%
  dplyr::arrange(desc(chatP), by_group = TRUE) %>%
  slice_head(n = 5) %>%
  ungroup() -> df.plot

x = construct_Network_df(df = df.plot,
                         category = "All",
                         restrict.by = "Both")

# pdf(paste0(output.dir, "CAOC_treeplot_SiVa_forward_male_LTB4_IGFBP5.pdf"), width = 12, height = 8)

network_treeplot(x)

# dev.off()
```



```{r}
df.plot = CAOC_SiVa@net$male$forward$immune_to_stromal
df.plot = df.plot[df.plot$LS_name %in% unique(CAOC_SiVa@DEpath[CAOC_SiVa@DEpath$Direction == "forward", ]$LS_name)[c(17, 12, 4, 31)] &
                    df.plot$Target %in% c("IGFBP5", "MMP2", "COL1A2", "PODXL", "SRGN"), ]

# pdf(paste0(output.dir, "CAOC_rosediagram_SiVa_forward_male_immune_stromal.pdf"), width = 12, height = 8)

components_rosediagram(df = df.plot, 
                       category = "All",
                       n = 5)

# dev.off()
```


```{r}
# pdf(paste0(output.dir, "SL_CAOC_riverplot_SiVa_male_forward_imm_to_stromal.pdf"), width = 12, height = 6)

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)

# dev.off()
```


# Comparative analysis (Lymph node, Vasculature)

## Create data inputs
```{r, include=FALSE}
data.list = list()
idents.list = list()
conditions.list = list()

organs = c("Lymph_Node", "Vasculature")
conditions = c("female", "male")

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  
  Data.input_organ <- TS_Data_list[[organ.select]]
  data.list[[i]] = Data.input_organ@assays$RNA@data

  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition
  conditions.list[[i]] = Data.input_organ@active.ident
}


metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}
```



```{r}
markergenes = read_csv(paste0(data.path, "humanatlas_markergenes_5organs.csv") )

N = 15

targets = c()

for (i in 1:length(organs)) {
  
  markergenes.organ = markergenes[markergenes$organ == organs[i], ]
  markergenes.organ %>%
    group_by(marker_ID) %>%
    dplyr::filter(avg_log2FC > 1) %>%
    slice_head(n = N) %>%
    ungroup() -> top.markers
  
  targets = c(targets, top.markers$gene)
}

targets = unique(targets)
```

## Analysis
Create OC object
```{r}
CAOC = create_OrganChat(object = data.list, 
                          organs = organs, 
                          idents.list = idents.list,
                          ComparisonAnalysis = TRUE,
                          conditions = conditions,
                          conditions.list = conditions.list,
                          assay = NULL, 
                          do.sparse = T)
```


Integrate metabolite data
```{r}
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)
```


Calculate the expression level using the scRNA-seq data
```{r}
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)
```

Infer signaling paths
```{r}
CAOC = CA_net0_infer(object = CAOC,
                         DB = OrganChatDB, 
                         LS = NULL, 
                         receptor = NULL, 
                         tf = NULL,
                         target = targets)
```

Analysis
```{r}
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.2, 0.2, 0.2),
                       CA_cutoff_chatP = 0.2,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)
```


Infer DEpath
```{r}
CAOC = DEpath_table(object = CAOC,
                        Sender.group = NULL,
                        Receiver.group = NULL,
                        Direction = NULL,
                        p_cutoff = NULL,
                        sd_cutoff = NULL,
                        DI_cutoff = NULL,
                        top = NULL)
```


```{r}
CAOC_LnVa = CAOC

# saveRDS(CAOC_LnVa, file = paste0(data.path, "CAOC_LnVa.rds"))
```


## Visualization
Chorddiagram
```{r}
CAOC_chorddiagram(object = CAOC_LnVa,
                  dir = "forward",
                  category = "All",
                  style = "ave.weight",
                  chatP_cutoff = 0.75)

```


```{r}
df.plot = CAOC_LnVa@net$female$forward$immune_to_stromal
df.plot = df.plot[df.plot$chatP > 0.5, ]

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```



```{r}
df.plot = CAOC_LnVa@net$female$forward$endothelial_to_endothelial
df.plot = df.plot[df.plot$chatP > 0.5, ]

OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 10,
             text.color = FALSE,
             LS_name = TRUE)
```


```{r}
df.plot = df.plot[df.plot$LS_name == "L-Lactic acid" & df.plot$Target == "VWF" & df.plot$chatP > 0.75, ]

# pdf(paste0(output.dir, "CAOC_treeplot_LnVa_female_forward_LLacticacid_VWF.pdf"), width=12, height = 8)

x = construct_Network_df(df = df.plot,
                         category = "All",
                         restrict.by = "Both")
network_treeplot(x)

# dev.off()
```



```{r}
OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 3,
             text.color = FALSE,
             LS_name = TRUE)
```


```{r}
CAOC_bubbleheatmap(object = CAOC_LnVa,
                   dir = "backward",
                   category = "All",
                   chatP_cutoff = 0.1,
                   size = "total.counts",
                   color = "total.chatP")
```


```{r}
OC_bubbleheatmap(object = CAOC_LnVa,
                net = CAOC_LnVa@net$female$backward,
                dir = "backward",
                category = "All",
                size = "total.counts",
                color = "total.chatP")
```
