---
title: "HumanAtlas_Science_2022_DataProcessing"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{HumanAtlas_Science_2022_DataProcessing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Data processing includes: (1) converting the h5ad files into Seurat objects; (2) separating the data by gender and down-sampling.

All processed data at the following Zenodo repository: https://doi.org/10.5281/zenodo.19042679.

The original data comes from the following paper: Claire L. Walsh et al. ,The Human Organ Atlas.Sci. Adv.12,eadz2240(2026).DOI:10.1126/sciadv.adz2240.

```{r setup}
library(OrganChat)

library(scCustomize)
library(sceasy)
```


Convert the h5ad files into Seurat objects
```{r}
organ.list <- c("Thymus", "Spleen", "Small_Intestine", "Prostate", "Lymph_Node", "Bladder", "Liver")
CAOC.organ.list <- c("Lung", "Vasculature", "Blood", "Spleen", "Small_Intestine", "Lymph_Node", "Bladder")

for (i in 1:length(CAOC.organ.list)) {
  ad_path <- paste0("/Volumes/Samsung_T5/OrganChat/Examples/HumanAtlas_Science_2022/OriginalData/TS_", organ.list[i], ".h5ad")
  rds_path <- paste0("/Volumes/Samsung_T5/OrganChat/Examples/HumanAtlas_Science_2022/OriginalData/TS_", organ.list[i], ".rds")
  
  sceasy::convertFormat(ad_path, from="anndata", to="seurat", outFile=rds_path)
}
```

Load and scale the seurat objects
```{r}
TS_Data_list = list()

for (i in 1:length(CAOC.organ.list)) {
  TS_Data_list[[i]] <- readRDS(paste0("/Volumes/Samsung_T5/OrganChat/Examples/HumanAtlas_Science_2022/OriginalData/TS_", organ.list[i], ".rds"))
}

names(TS_Data_list) = CAOC.organ.list
```

Select data from donor 2 (F) and 14 (M)
```{r}
for (i in 1:length(TS_Data_list)) {
  TS_Data_list[[i]] <- subset(TS_Data_list[[i]], subset = donor %in% c("TSP2", "TSP14"))
}
```

Construct a list of gender-specific data
```{r}
# c(2,3,5,6)
TS_genderData_list <- list()

for (i in 1:length(CAOC.organ.list)) {
  df.list = list(female = list(), male = list())
  
  seurat.object = TS_Data_list[[CAOC.organ.list[i]]]
  
  df.list[["female"]] = subset(seurat.object, subset = gender == "female")
  df.list[["male"]] = subset(seurat.object, subset = gender == "male")
  
  TS_genderData_list[[i]] = df.list
}
names(TS_genderData_list) = CAOC.organ.list
```



```{r}
for (i in 1:length(TS_genderData_list)) {

  print(table(TS_genderData_list[[i]]$female$compartment))
  print(table(TS_genderData_list[[i]]$male$compartment))
}
```


Down-sampling
```{r}
TS_subset_genderData_list = TS_genderData_list

downsample.rate = 0.25
mincells = 200

for (i in 1:length(TS_genderData_list)) {
  for (j in 1:2) {
    # select the seurat object
    datause <- TS_genderData_list[[i]][[j]]
    metause <- TS_genderData_list[[i]][[j]]@meta.data
    # select clusters with >200 cells
    cluster = names(table(datause$compartment)[table(datause$compartment)>mincells])
    # down-sampling
    cellbarcodes = colnames(datause@assays$RNA@data)
    rownames(metause) = cellbarcodes
    remove_cells <- c()
    for (k in 1:length(cluster)) {
      # cell barcodes of the down-sampled cluster
      metause_downsample = metause[metause$compartment == cluster[k], ]
      # cells that need to be removed
      if(nrow(metause_downsample)>6000){
        cellbarcodes_downsample = rownames( metause_downsample[sample( nrow(metause_downsample), floor(nrow(metause_downsample)*(1-downsample.rate*0.6)) ), ] )
      }else{
        cellbarcodes_downsample = rownames( metause_downsample[sample( nrow(metause_downsample), floor(nrow(metause_downsample)*(1-downsample.rate)) ), ] )
      }
      # barcodes of the cells to be removed
      remove_cells <- c(remove_cells, cellbarcodes_downsample)
    }
    cellbarcodes = cellbarcodes[!(cellbarcodes %in% remove_cells)]
    data.output = subset(datause, cells = cellbarcodes)
    # add cell type label
    data.output@meta.data$Type = as.factor(data.output@meta.data$compartment)
    data.output@meta.data$Type = fct_drop(data.output@meta.data$Type)
    # remove cluster with <200 cells
    # cluster.table = table(data.output@meta.data$Type)
    # Type.select = names(cluster.table[cluster.table>mincells])
    # data.output = subset(data.output, subset = Type %in% Type.select)
    # data.output@meta.data$Type = fct_drop(data.output@meta.data$Type)
    # add condition label
    data.output@meta.data$condition = names(TS_subset_genderData_list[[i]][j])
      
    TS_subset_genderData_list[[i]][[j]] = data.output
  }
}
```



```{r}
for (i in 1:length(TS_subset_genderData_list)) {

  print(table(TS_subset_genderData_list[[i]]$female$Type))
  print(table(TS_subset_genderData_list[[i]]$male$Type))
}
```


Merge and save
```{r}
path = yourpath
for (i in 1:length(TS_subset_genderData_list)) {
  merged_object <- Merge_Seurat_List(list_seurat = TS_subset_genderData_list[[i]])
  
  # saveRDS(merged_object, paste0(path, "TS_", names(TS_subset_genderData_list[i]), "_downsampled.rds"))
}
```
