---
title: "ValidationData_NewAnalysis_032026"
output: html_document
date: "2026-03-18"
---

This extended analysis for Liver - Skin communications includes two rounds of OrganChat inference: (1) targets are the top 30 markers of each Skin cluster of both conditions; (2) targets are the top 30 markers of each Liver cluster of both conditions.

Due to the large number of targets, this process can take extensive time. But you can directly load and explore the saved objects from Zenodo.

```{r}
library(OrganChat)
```

# Load required data & database


```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse_ExtendedAnalysis/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse_ExtendedAnalysis/"    # your path to the ouput folder
```

Load metabolite dictionary data
```{r, include=FALSE}
hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```


Load the Seurat object, which will be stored in a list
c("Liver", "Skin", "Adipose")
```{r}
organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

UCI_Data_list <- list()

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] = readRDS(paste0(data.path, "UCI_", organ.list[i], "_downsampled.rds"))
}

names(UCI_Data_list) = organ.list
```


Merge "old_resistant", "old_sensitive" for new "old" condition
```{r}
for (i in 1:3) {
  UCI_Data_list[[i]]$condition_2 = UCI_Data_list[[i]]$condition
  UCI_Data_list[[i]]$condition_2[UCI_Data_list[[i]]$condition_2 == "old_resistant" | UCI_Data_list[[i]]$condition_2 == "old_sensitive"] = "old"
}
```

################################################################################

# Liver-Skin analysis with Skin marker genes as the targets

## Target selection
young
```{r}
Data.use.1 = subset(UCI_Data_list[["Skin"]], 
                    subset = condition_2 == "young" ) 
Data.use.1 <- SetIdent(Data.use.1, value = Data.use.1$Type)

# infer markers 
markers.Type <- FindAllMarkers(Data.use.1, only.pos = FALSE)

# the total number of targets will be ~5N
N = 30

markers.Type %>%
  group_by(cluster) %>%
  dplyr::arrange(abs(avg_log2FC)) %>%
  slice_head(n = N) %>%
  ungroup() -> top.markers

target.1 = unique(top.markers$gene)
```

old
```{r}
Data.use.1 = subset(UCI_Data_list[["Skin"]], 
                    subset = condition_2 == "old" ) 
Data.use.1 <- SetIdent(Data.use.1, value = Data.use.1$Type)

# infer markers 
markers.Type <- FindAllMarkers(Data.use.1, only.pos = FALSE)

# the total number of targets will be ~5N
N = 30

markers.Type %>%
  group_by(cluster) %>%
  dplyr::arrange(abs(avg_log2FC)) %>%
  slice_head(n = N) %>%
  ungroup() -> top.markers

target.2 = unique(top.markers$gene)
```

merge
```{r}
target = unique(c(target.1, target.2))
```


## CAOC analysis

Setup organs & conditions
```{r}
# organs for validation
S.organ = "Liver"
R.organ = "Skin"

# conditions for validation
conditions = c("young", "old")
```


```{r, include=FALSE}
organs = c(S.organ, R.organ)

data.list = list()
idents.list = list()
conditions.list = list()

for (i in 1:length(organs)) {
  
  organ.select = organs[i]
  # select subset data of the two conditions
  Data.input_organ <- UCI_Data_list[[organ.select]]
  
  data.list[[i]] = Data.input_organ@assays$RNA@data
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$Type
  idents.list[[i]] = Data.input_organ@active.ident
  
  Idents(Data.input_organ) = Data.input_organ@meta.data$condition_2
  conditions.list[[i]] = Data.input_organ@active.ident
}

# Create OC object
CAOC = create_OrganChat(object = data.list, 
                        organs = organs, 
                        idents.list = idents.list,
                        ComparisonAnalysis = TRUE,
                        conditions = conditions,
                        conditions.list = conditions.list,
                        assay = NULL, 
                        do.sparse = T)

# Calculate the expression level using the scRNA-seq data
CAOC = CA_cal_scRNA.bygroup(object = CAOC,
                            DB = OrganChatDB,
                            mean_method = NULL,
                            scale.max = 10)

# Prepare the metabolite flux data
organs = CAOC@organs

metalist.1 = list()
metalist.2 = list()

for (i in 1:length(organs)) {
  organ.select = organs[i]
  metalist.1[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[1],".csv") )
  metalist.1[[i]] <- as.data.frame(metalist.1[[i]])
  rownames(metalist.1[[i]]) <- metalist.1[[i]][, 1]
  metalist.1[[i]] <- metalist.1[[i]][, -1]
  
  metalist.2[[i]] = read_csv( paste0(data.path, organ.select, "_flux_", conditions[2],".csv"))
  metalist.2[[i]] <- as.data.frame(metalist.2[[i]])
  rownames(metalist.2[[i]]) <- metalist.2[[i]][, 1]
  metalist.2[[i]] <- metalist.2[[i]][, -1]
}

# Integrate metabolite data
CAOC = CA_merge_metabolite.bygroup(object = CAOC,
                                   metabolitedata.list.condition1 = metalist.1,
                                   metabolitedata.list.condition2 = metalist.2,
                                   type = "flux",
                                   scale.max = 10)

################################################################################
LS.names = c()
DG.names = c()

for (i in 1:length(conditions)) {

  LS.1 = CAOC@LSdata[[i]][[1]]
  LS.2 = CAOC@LSdata[[i]][[2]]

  DG.1 = CAOC@DGdata[[i]][[1]]
  DG.2 = CAOC@DGdata[[i]][[2]]

  LS.1$sum = apply(LS.1[ , 1:(ncol(LS.1)-1)], 1, sum)
  LS.2$sum = apply(LS.2[ , 1:(ncol(LS.2)-1)], 1, sum)
  DG.1$sum = apply(DG.1, 1, sum)
  DG.2$sum = apply(DG.2, 1, sum)

  LS.names = unique( c(LS.names, rownames(LS.1[LS.1$sum>0, ]), rownames(LS.2[LS.2$sum>0, ])) )
  DG.names = unique( c(DG.names, rownames(DG.1[DG.1$sum>0, ]), rownames(DG.2[DG.2$sum>0, ])) )
}
################################################################################

# Infer signaling paths
CAOC = CA_net0_infer(object = CAOC,
                     DB = OrganChatDB, 
                     LS = LS.names, 
                     receptor = DG.names, 
                     tf = DG.names,
                     target = target)

# Analysis
CAOC = CA_net_analysis(object = CAOC,
                       K = 0.1, 
                       N = 1,
                       R = 100,
                       CI = 0.95,
                       CA_cutoff_value = c(0, 0.1, 0.1, 0.1),
                       CA_cutoff_chatP = NULL,
                       CA_cutoff_sd = NULL,
                       CA_cutoff_CI = 0)

# Infer DEpath
CAOC = DEpath_table(object = CAOC,
                    Sender.group = NULL,
                    Receiver.group = NULL,
                    Direction = NULL,
                    p_cutoff = NULL,
                    sd_cutoff = NULL,
                    DI_cutoff = NULL,
                    top = NULL)

# save the "object_list"
# saveRDS(CAOC, file = paste0(data.path, "CAOC_NewAnalysis_LiverSkin_032026.rds"))
```


## Pathway filtering -- liver to adipose
```{r}
object = CAOC

list_1 = object@net[[1]]$forward
list_2 = object@net[[2]]$forward
list.new = list()

for (i in 1:length(list_1)) {
  df1 = list_1[[i]]
  df2 = list_2[[i]]
  
  df.new = df1[ , 1:10]
  df.new$LS.value_Y = df1$LS.value
  df.new$LS.value_O = df2$LS.value
  df.new$Target.value_Y = df1$Target.value
  df.new$Target.value_O = df2$Target.value
  df.new$chatP_Y = df1$chatP
  df.new$chatP_O = df2$chatP
  
  df.new = df.new[(df.new$chatP_Y>0.2 | df.new$chatP_O>0.2), ]
  
  list.new[[i]] = df.new
}

pathway_YO = rbindlist(list.new)
pathway_YO$LS.change_YO = pathway_YO$LS.value_Y - pathway_YO$LS.value_O
pathway_YO$Target.change_YO = pathway_YO$Target.value_Y - pathway_YO$Target.value_O
pathway_YO$chatP.change_YO = pathway_YO$chatP_Y - pathway_YO$chatP_O

pathway_YO = pathway_YO[ abs(pathway_YO$LS.change_YO)>0.05 & abs(pathway_YO$chatP.change_YO)>0.05, ]

pathway_YO = pathway_YO[pathway_YO$LS.change_YO*pathway_YO$chatP.change_YO>0 & pathway_YO$Target.change_YO*pathway_YO$chatP.change_YO>0, ]
```


```{r}
pathway_YO$LS_changeinOld = "up"
pathway_YO$LS_changeinOld[pathway_YO$LS.change_YO>0] = "down"

pathway_YO$Target_changeinOld = "up"
pathway_YO$Target_changeinOld[pathway_YO$Target.change_YO>0] = "down"

df = data.frame(LS_name = pathway_YO$LS_name, Receptior = pathway_YO$Receptor, 
                Sender.group = pathway_YO$Sender.group, Receiver.group = pathway_YO$Receiver.group,
                LS_changeinOld = pathway_YO$LS_changeinOld, Target_changeinOld = pathway_YO$Target_changeinOld)
df = df[!duplicated(df),]
```

Save the results
```{r}
# write.csv(pathway_YO, file = paste0(output.path, "Liver_Skin_YoungOld_032026.csv"))
# write.csv(df, file = paste0(output.path, "Liver_Skin_YoungOld_LS_R_032026.csv"))
```


