---
title: "ValidationData_NewAnalysis_LRexplore_AdditionalFigures_04182026"
output: html_document
date: "2026-04-18"
---

```{r}
library(scales)
library(plotrix)
library(Seurat)
library(qtl2)
library(readr)
library(dplyr)
library(forcats)
```


# Load required data & database


```{r}
data.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse_ExtendedAnalysis/"     # your path to the data
DB.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/OrganChatDB/"                   # your path to the OrganChatDB
Dictionary.path = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Metabolite_Dictionary/" # your path to the files "hmdb_dictionary" and "METAFlux_lookup"
output.dir = "~/Research_2025/OrganChat_v3/Nature_submission/Zenodo/Insulin_UCI_2025_mouse_ExtendedAnalysis/"    # your path to the ouput folder
```

Load metabolite dictionary data
```{r, include=FALSE}
OrganChatDB_hmdb_dictionary <- read_csv(paste0(Dictionary.path, "hmdb_dictionary_20240129.csv"))
METAFlux_lookup <- read_csv(paste0(Dictionary.path, "METAFlux_lookup_20240131.csv"))
```


Load OCDB
```{r}
# load database
load(paste0(DB.path, "LSR_layer1_mouse.rda"))
load(paste0(DB.path, "RSE_layer2_mouse.rda"))
load(paste0(DB.path, "SET_layer3_mouse.rda"))

OrganChatDB <- list()
OrganChatDB[[1]] <- LSR_layer1_mouse
OrganChatDB[[2]] <- RSE_layer2_mouse
OrganChatDB[[3]] <- SET_layer3_mouse
```


Load the Seurat object, which will be stored in a list
c("Liver", "Skin", "Adipose")
```{r}
organ.list = c("Liver", "Skin", "Adipose")
condition.list = c("old_resistant", "old_sensitive", "young")

UCI_Data_list <- list()

for (i in 1:length(organ.list)) {
  UCI_Data_list[[i]] = readRDS(paste0(data.path, "UCI_", organ.list[i], "_downsampled.rds"))
}


names(UCI_Data_list) = organ.list
```


Merge "old_resistant", "old_sensitive" for new "old" condition
```{r}
for (i in 1:3) {
  UCI_Data_list[[i]]$condition_2 = UCI_Data_list[[i]]$condition
  UCI_Data_list[[i]]$condition_2[UCI_Data_list[[i]]$condition_2 == "old_resistant" | UCI_Data_list[[i]]$condition_2 == "old_sensitive"] = "old"
}
```


# Visuzlizations

Load the objects: Liver to Skin/Adipose (Targets: top 30 markers of each group in every condition)
```{r}
CAOC_LiSk = readRDS(paste0(data.path, "CAOC_NewAnalysis_LiverSkin_032026.rds"))
CAOC_LiAd = readRDS(paste0(data.path, "CAOC_NewAnalysis_LiverAdipose_032026.rds"))
```

# Visuzlizations

chord diagram
```{r}
# pdf(paste0(output.path, "CAOC_chorddiagram_LiSk_forward_AllSignals_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiSk,
                  dir = "forward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiAd_forward_AllSignals_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiAd,
                  dir = "forward",
                  category = "All",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiSk_forward_metabolite_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiSk,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiAd_forward_metabolite_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiAd,
                  dir = "forward",
                  category = "metabolite",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# cytokines
# pdf(paste0(output.path, "CAOC_chorddiagram_LiSk_forward_cytokines_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiSk,
                  dir = "forward",
                  category = "cytokines",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiAd_forward_cytokines_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiAd,
                  dir = "forward",
                  category = "cytokines",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# hormone_nonpeptide
# pdf(paste0(output.path, "CAOC_chorddiagram_LiSk_forward_hormone_nonpeptide_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiSk,
                  dir = "forward",
                  category = "hormone_nonpeptide",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiAd_forward_hormone_nonpeptide_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiAd,
                  dir = "forward",
                  category = "hormone_nonpeptide",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# hormone_peptide
# pdf(paste0(output.path, "CAOC_chorddiagram_LiSk_forward_hormone_peptide_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiSk,
                  dir = "forward",
                  category = "hormone_peptide",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# pdf(paste0(output.path, "CAOC_chorddiagram_LiAd_forward_hormone_peptide_totalcounts_075.pdf"), width=8, height = 12)
CAOC_chorddiagram(object = CAOC_LiAd,
                  dir = "forward",
                  category = "hormone_peptide",
                  style = "total.counts",
                  chatP_cutoff = 0.75)

# dev.off(); dev.off(); dev.off(); dev.off()
# dev.off(); dev.off(); dev.off(); dev.off()
# dev.off()
# dev.off()
```

riverplot
```{r}
# LiSk
df.plot = CAOC_LiSk@net$young$forward$`EC_to_Sebaceous gland`
# pdf(paste0(output.path, "CAOC_riverplot_LiSk_young_forward_EC_to_Sebaceous.pdf"), width = 12, height = 6)
OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)

df.plot = CAOC_LiSk@net$old$forward$`EC_to_Sebaceous gland`
# pdf(paste0(output.path, "CAOC_riverplot_LiSk_old_forward_EC_to_Sebaceous.pdf"), width = 12, height = 6)
OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)

# LiAd
df.plot = CAOC_LiAd@net$young$forward$`zone 2_to_Mesenchymal progenitors`
# pdf(paste0(output.path, "CAOC_riverplot_LiAd_young_forward_zone2_to_Mesenchymal.pdf"), width = 12, height = 6)
OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)

df.plot = CAOC_LiAd@net$old$forward$`zone 2_to_Mesenchymal progenitors`
# pdf(paste0(output.path, "CAOC_riverplot_LiAd_old_forward_zone2_to_Mesenchymal.pdf"), width = 12, height = 6)
OC_riverplot(df = df.plot,
             pref = "LS",
             category = "All",
             n.path = 20,
             text.color = FALSE,
             LS_name = TRUE)

# dev.off()
# dev.off()
# dev.off()
# dev.off()
```

bubleheatmap
```{r}
# All signals
# pdf(paste0(output.path, "CAOC_bubleheatmap_LiSk_forward_AllSignals_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiSk,
                  dir = "forward",
                  category = "All",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# pdf(paste0(output.path, "CAOC_bubleheatmap_LiAd_forward_AllSignals_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiAd,
                  dir = "forward",
                  category = "All",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# metabolite
# pdf(paste0(output.path, "CAOC_bubleheatmap_LiSk_forward_metabolite_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiSk,
                  dir = "forward",
                  category = "metabolite",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# pdf(paste0(output.path, "CAOC_bubleheatmap_LiAd_forward_metabolite_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiAd,
                  dir = "forward",
                  category = "metabolite",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# cytokines
# pdf(paste0(output.path, "CAOC_bubleheatmap_LiSk_forward_cytokines_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiSk,
                  dir = "forward",
                  category = "cytokines",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# pdf(paste0(output.path, "CAOC_bubleheatmap_LiAd_forward_cytokines_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiAd,
                  dir = "forward",
                  category = "cytokines",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# hormone_nonpeptide
# pdf(paste0(output.path, "CAOC_bubleheatmap_LiSk_forward_hormone_nonpeptide_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiSk,
                  dir = "forward",
                  category = "hormone_nonpeptide",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# pdf(paste0(output.path, "CAOC_bubleheatmap_LiAd_forward_hormone_nonpeptide_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiAd,
                  dir = "forward",
                  category = "hormone_nonpeptide",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# hormone_peptide
# pdf(paste0(output.path, "CAOC_bubleheatmap_LiSk_forward_hormone_peptide_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiSk,
                  dir = "forward",
                  category = "hormone_peptide",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# pdf(paste0(output.path, "CAOC_bubleheatmap_LiAd_forward_hormone_peptide_chatP_05.pdf"), width = 12, height = 6)
CAOC_bubbleheatmap(object = CAOC_LiAd,
                  dir = "forward",
                  category = "hormone_peptide",
                  chatP_cutoff = 0.5,
                  size = "total.counts",
                  color = "ave.weight")

# dev.off(); dev.off(); dev.off(); dev.off()
# dev.off(); dev.off(); dev.off(); dev.off()
# dev.off(); dev.off()
```


################################################################################

DEpaths
```{r}
DEpath_LiSk = read_csv(paste0(data.path, "Liver_Skin_YoungOld_032026.csv"))
DEpath_LiAd = read_csv(paste0(data.path, "Liver_Adipose_YoungOld_032026.csv"))
```


```{r}
DEpath_LiSk %>%
    group_by(LS) %>%
    dplyr::arrange(-abs(chatP.change_YO)) %>% 
    slice_head(n = 1) %>%
    ungroup() -> DEpath_LiSk_top1

DEpath_LiAd %>%
    group_by(LS) %>%
    dplyr::arrange(-abs(chatP.change_YO)) %>% 
    slice_head(n = 1) %>%
    ungroup() -> DEpath_LiAd_top1

df.plot_LiSk = inner_join(CAOC_LiSk@DEpath, DEpath_LiSk_top1[ , c("Path", "Sender.group", "Receiver.group")], 
                     by = c("Path", "Sender.group", "Receiver.group"))

df.plot_LiAd = inner_join(CAOC_LiAd@DEpath, DEpath_LiAd_top1[ , c("Path", "Sender.group", "Receiver.group")], 
                     by = c("Path", "Sender.group", "Receiver.group"))
```



DI_barplot
```{r}
CAOC_DI_barplot(df = df.plot_LiSk,
                n = 3,
                axis.text.size = 50)

CAOC_DI_barplot(df = df.plot_LiAd,
                n = 3,
                axis.text.size = 50)

```

